---
title: "Mid-Atl Clean"
author: "Annie Smith"
date: "2025-11-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

#libraries

```{r}
library(PAMscapes)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(here)
library(dplyr)
library(car)
library(patchwork)
library(ggpubr)
library(rstatix)
library(PAMmisc)
library(dunn.test)
library(smplot2)
library(tsibble)
library(scales)
library(ggpmisc)
library(paletteer)
library(ggh4x)
library(suntools)
library(zoo)
library(wesanderson)
library(openair)
library(directlabels)

```
#loading full HMD files per site
```{r}
DB01_HMD <- read.csv(here("data/DB01_HMD.csv"))
DB01_HMD$UTC <- as.POSIXct(DB01_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB01_HMD$PLATFORM = "DB01"
DB02_HMD <- read.csv(here("data/DB02_HMD.csv"))
DB02_HMD$UTC <- as.POSIXct(DB02_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB02_HMD$PLATFORM = "DB02"
DB03_HMD <- read.csv(here("data/DB03_HMD.csv"))
DB03_HMD$UTC <- as.POSIXct(DB03_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB03_HMD$PLATFORM = "DB03"

ES01_HMD <- read.csv(here("data/ES01_HMD.csv"))
ES01_HMD$UTC <- as.POSIXct(ES01_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES01_HMD$PLATFORM = "ES01"
ES02_HMD <- read.csv(here("data/ES02_HMD.csv"))
ES02_HMD$UTC <- as.POSIXct(ES02_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES02_HMD$PLATFORM = "ES02"
ES03_HMD <- read.csv(here("data/ES03_HMD.csv"))
ES03_HMD$UTC <- as.POSIXct(ES03_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES03_HMD$PLATFORM = "ES03"

CB01_HMD <- read.csv(here("data/CB01_HMD.csv"))
CB01_HMD$UTC <- as.POSIXct(CB01_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB01_HMD$PLATFORM = "CB01"
CB02_HMD <- read.csv(here("data/dataCB02_HMD.csv"))
CB02_HMD$UTC <- as.POSIXct(CB02_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB02_HMD$PLATFORM = "CB02"
CB03_HMD <- read.csv(here("data/CB03_HMD.csv"))
CB03_HMD$UTC <- as.POSIXct(CB03_HMD$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB03_HMD$PLATFORM = "CB03"
```
#loading in OL files per site
```{r}
DB01_OL <- read.csv(here("data/DB01_OL.csv"))
DB01_OL <- DB01_OL[-c(1)]
DB01_OL$UTC_fixed <- paste(DB01_OL$UTC_date, DB01_OL$UTC_hour, sep = " ")
DB01_OL$UTC_fixed <- as.POSIXct(DB01_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
DB01_OL$PLATFORM = "DB01"
DB01_OL$shore = "Inshore"
DB01_OL$Lat = "Delaware"

DB02_OL <- read.csv(here("data/DB02_OL.csv"))
DB02_OL <- DB02_OL[-c(1)]
DB02_OL$UTC_fixed <- paste(DB02_OL$UTC_date, DB02_OL$UTC_hour, sep = " ")
DB02_OL$UTC_fixed <- as.POSIXct(DB02_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
DB02_OL$PLATFORM = "DB02"
DB02_OL$shore = "Mid-shore"
DB02_OL$Lat = "Delaware"

DB03_OL <- read.csv(here("data/DB03_OL.csv"))
DB03_OL <- DB03_OL[-c(1)]
DB03_OL$UTC_fixed <- paste(DB03_OL$UTC_date, DB03_OL$UTC_hour, sep = " ")
DB03_OL$UTC_fixed <- as.POSIXct(DB03_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
DB03_OL$PLATFORM = "DB03"
DB03_OL$shore = "Offshore"
DB03_OL$Lat = "Delaware"

ES01_OL <- read.csv(here("data/ES01_OL.csv"))
ES01_OL <- ES01_OL[-c(1)]
ES01_OL$UTC_fixed <- paste(ES01_OL$UTC_date, ES01_OL$UTC_hour, sep = " ")
ES01_OL$UTC_fixed <- as.POSIXct(ES01_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
ES01_OL$PLATFORM = "ES01"
ES01_OL$shore = "Inshore"
ES01_OL$Lat = "Eastern"

ES02_OL <- read.csv(here("data/ES02_OL.csv"))
ES02_OL <- ES02_OL[-c(1)]
ES02_OL$UTC_fixed <- paste(ES02_OL$UTC_date, ES02_OL$UTC_hour, sep = " ")
ES02_OL$UTC_fixed <- as.POSIXct(ES02_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
ES02_OL$PLATFORM = "ES02"
ES02_OL$shore = "Mid-shore"
ES02_OL$Lat = "Eastern"

ES03_OL <- read.csv(here("data/ES03_OL.csv"))
ES03_OL <- ES03_OL[-c(1)]
ES03_OL$UTC_fixed <- paste(ES03_OL$UTC_date, ES03_OL$UTC_hour, sep = " ")
ES03_OL$UTC_fixed <- as.POSIXct(ES03_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
ES03_OL$PLATFORM = "ES03"
ES03_OL$shore = "Offshore"
ES03_OL$Lat = "Eastern"

CB01_OL <- read.csv(here("data/CB01_OL.csv"))
CB01_OL <- CB01_OL[-c(1)]
CB01_OL$UTC_fixed <- paste(CB01_OL$UTC_date, CB01_OL$UTC_hour, sep = " ")
CB01_OL$UTC_fixed <- as.POSIXct(CB01_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
CB01_OL$PLATFORM = "CB01"
CB01_OL$shore = "Inshore"
CB01_OL$Lat = "Chesapeake"


CB02_OL <- read.csv(here("data/CB02_OL.csv"))
str_split(CB02_OL$UTC[2]," ", simplify = T)[,1]
str_split(CB02_OL$UTC[2]," ", simplify = T)[,2]
CB02_OL <- CB02_OL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2]) %>%
  mutate(UTC_fixed = NA)
CB02_OL %>% filter(UTC_hour == "")
CB02_OL %>% filter(UTC_hour == "") %>% nrow # 843 rows having missing hour
# Find empty rows in new columns and fill in 
for (c in 1:nrow(CB02_OL)) { # for each row
  if (CB02_OL$UTC_hour[c] == "") { # if the hour column was left empty
    CB02_OL$UTC_hour[c] <- "00:00:00" # manually add midnight
  }
}
CB02_OL$UTC_fixed <- paste(CB02_OL$UTC_date, CB02_OL$UTC_hour, sep = " ")
CB02_OL$UTC_fixed <- as.POSIXct(CB02_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
CB02_OL <- CB02_OL[-c(1)]
CB02_OL$PLATFORM = "CB02"
CB02_OL$shore = "Mid-shore"
CB02_OL$Lat = "Chesapeake"

CB03_OL <- read.csv(here("data/CB03_OL.csv"))
CB03_OL <- CB03_OL[-c(1)]
CB03_OL$UTC_fixed <- paste(CB03_OL$UTC_date, CB03_OL$UTC_hour, sep = " ")
CB03_OL$UTC_fixed <- as.POSIXct(CB03_OL$UTC_fixed, format = "%Y-%m-%d %H:%M:%S")
CB03_OL$PLATFORM = "CB03"
CB03_OL$shore = "Mid-shore"
CB03_OL$Lat = "Chesapeake"

```
#chorus presence files
```{r}
#DB01
DB01_chorusPresence <- read.csv(here("data/DB01_chorusPresence.csv"))
DB01_chorusPresence$date <- as.Date(DB01_chorusPresence$date, format= "%m/%d/%Y")
colnames(DB01_chorusPresence)[1] <- "UTC"
DB01_chorusPresence$site = "DB01"
colnames(DB01_chorusPresence)[5] <- "toadfish_chorus"

DB02_chorusPresence <- read.csv(here("data/DB02_chorusPresence.csv"))
DB02_chorusPresence$date <- as.Date(DB02_chorusPresence$date, format= "%m/%d/%Y")
colnames(DB02_chorusPresence)[1] <- "UTC"
DB02_chorusPresence$site = "DB02"

DB03_chorusPresence <- read.csv(here("data/DB03_chorusPresence.csv"))
DB03_chorusPresence <- DB03_chorusPresence[-c(7)]
DB03_chorusPresence$date <- as.Date(DB03_chorusPresence$date, format= "%m/%d/%Y")
colnames(DB03_chorusPresence)[1] <- "UTC"
DB03_chorusPresence$site = "DB03"
colnames(DB03_chorusPresence)[6] <- "offshore_chorus"

ES01_chorusPresence <- read.csv(here("data/ES01_chorusPresence.csv"))
ES01_chorusPresence$date <- as.Date(ES01_chorusPresence$date, format= "%m/%d/%Y")
colnames(ES01_chorusPresence)[1] <- "UTC"
ES01_chorusPresence$site = "ES01"
colnames(ES01_chorusPresence)[5] <- "toadfish_chorus"

ES02_chorusPresence <- read.csv(here("data/ES02_chorusPresence.csv"))
ES02_chorusPresence$date <- as.Date(ES02_chorusPresence$date, format= "%m/%d/%Y")
colnames(ES02_chorusPresence)[1] <- "UTC"
ES02_chorusPresence$site = "ES02"

ES03_chorusPresence <- read.csv(here("data/ES03_chorusPresence.csv"))
ES03_chorusPresence$date <- as.Date(ES03_chorusPresence$date, format= "%m/%d/%Y")
colnames(ES03_chorusPresence)[1] <- "UTC"
ES03_chorusPresence$site = "ES03"
colnames(ES03_chorusPresence)[6] <- "offshore_chorus"

CB01_chorusPresence <- read.csv(here("data/CB01_chorusPresence.csv"))
CB01_chorusPresence$date <- as.Date(CB01_chorusPresence$date, format= "%m/%d/%Y")
colnames(CB01_chorusPresence)[1] <- "UTC"
CB01_chorusPresence$site = "CB01"
colnames(CB01_chorusPresence)[5] <- "toadfish_chorus"

CB02_chorusPresence <- read.csv(here("data/CB02_chorusPresence.csv"))
CB02_chorusPresence$date <- as.Date(CB02_chorusPresence$date, format= "%m/%d/%Y")
colnames(CB02_chorusPresence)[1] <- "UTC"
CB02_chorusPresence$site = "CB02"
colnames(CB02_chorusPresence)[5] <- "toadfish_chorus"


##COME BACK ONCE CB03 ERROR IS FIXED ON PYPAM##

CB03_chorusPresence <- read.csv(here("data/CB03_chorusPresence.csv"))
CB03_chorusPresence$date <- as.Date(CB03_chorusPresence$date, format= "%m/%d/%Y")
colnames(CB03_chorusPresence)[1] <- "UTC"
CB03_chorusPresence$site = "CB03"

```
#Seasonal PSD- figure 2
```{r}
 all_sites <- DB01_HMD%>%
  full_join(DB02_HMD)%>%
  full_join(DB03_HMD)%>%
  full_join(ES01_HMD)%>%
  full_join(ES02_HMD)%>%
  full_join(ES03_HMD)%>%
  full_join(CB01_HMD)%>%
  full_join(CB02_HMD)%>%
  full_join(CB03_HMD)

all_sites$month <- month(all_sites$UTC)

all_sites$season = case_when(all_sites$month == 1 ~ "Winter",
                            all_sites$month == 2 ~ "Winter",
                            all_sites$month == 3 ~ "Spring",
                            all_sites$month == 4 ~ "Spring",
                            all_sites$month == 5 ~ "Spring",
                            all_sites$month == 6 ~ "Summer",
                            all_sites$month == 7 ~ "Summer",
                            all_sites$month == 8 ~ "Summer",
                            all_sites$month == 9 ~ "Fall",
                            all_sites$month == 10 ~ "Fall",
                            all_sites$month == 11 ~ "Fall",
                            all_sites$month == 12 ~ "Winter")
 
all_sites$season = factor(all_sites$season,
                                        levels= c("Winter", "Spring", "Summer", "Fall"),
                                        labels= c("Winter", "Spring", "Summer", "Fall"))

all_sites$PLATFORM = factor(all_sites$PLATFORM,
                                        levels= c("DB01", "DB02", "DB03", "ES01", "ES02", "ES03", "CB01", "CB02", "CB03"),
                                        labels= c("DB01", "DB02", "DB03", "ES01", "ES02", "ES03", "CB01", "CB02", "CB03"))

#by season
plotPSD(x=all_sites, style='quantile', q= 0.1, by='season', facet='PLATFORM', quantileBorder= TRUE)+
  labs(y= (expression(paste("Power Spectral Density dB re 1 \u00b5Pa" ^ "2", "/Hz"))))+
  theme(axis.text= element_text(size= 10),
        axis.title= element_text(size= 14),
        legend.text = element_text(size= 13),
        legend.title= element_text(size= 13.5),
        strip.text= element_text(size= 12))+
  scale_color_manual(labels= c("Winter", "Spring", "Summer", "Fall" ), values= c("#5761C0", "#4B8320", "#DB2207","#FFAB38"))+
  scale_fill_manual(values= c("#5761C0", "#4B8320", "#DB2207","#FFAB38"))+
  theme_bw()+
  guides(color= guide_legend(title= "Season"))



```
#LTSA- supplemental
```{r}
allSites_LTSA = plotLTSA(x=all_sites, facet= 'PLATFORM', units= expression(paste("dB re 1 \u00b5Pa" ^ "2", "/Hz"))) +
  facet_grid(factor(PLATFORM, levels = c('DB01', 'DB02', 'DB03', 'ES01', 'ES02', 'ES03', 'CB01', 'CB02', 'CB03'))~.)+
  theme_bw()

plot(allSites_LTSA)

```
#plotAcousticScene- figure 3
```{r}
allSite_chorusPresence <- DB01_chorusPresence%>%
  full_join(ES01_chorusPresence)%>%
  full_join(CB01_chorusPresence) %>%
  full_join(DB02_chorusPresence) %>%
  full_join(ES02_chorusPresence) %>%
  full_join(CB02_chorusPresence) %>%
  full_join(DB03_chorusPresence) %>%
  full_join(ES03_chorusPresence) %>%
  full_join(CB03_chorusPresence)

  
colnames(allSite_chorusPresence)[2] <- "Unknown pulses"
colnames(allSite_chorusPresence)[3] <- "Unknown knocks"
colnames(allSite_chorusPresence)[4] <- "Cusk eel chorus"
colnames(allSite_chorusPresence)[5] <- "Toadfish chorus"
colnames(allSite_chorusPresence)[7] <- "Unknown offshore"

allSite_chorusPresenceFormatted <- loadDetectionData(x=allSite_chorusPresence, source='csv', detectionType='presence', wide=TRUE, 
tz='UTC', presenceDuration='1day', extraCols='site', 
speciesCols=c('Unknown pulses', 'Unknown knocks', 'Cusk eel chorus', 'Toadfish chorus', 'Unknown offshore'), detectedValues='1') #this formats csv file so it can be used for detectionExplorer



allSite_chorusPresenceFormatted$site = factor(allSite_chorusPresenceFormatted$site,
                                              levels= c("DB01", "DB02", "DB03", "ES01", "ES02", "ES03", "CB01", "CB02", "CB03"),
                                              labels= c("DB01", "DB02", "DB03", "ES01", "ES02", "ES03", "CB01", "CB02", "CB03"))

  
plotAcousticScene(x=allSite_chorusPresenceFormatted, by='site', combineYears=FALSE, freqMap=data.frame(species=c('Unknown knocks', 'Unknown pulses', 'Unknown offshore', 'Cusk eel chorus', 'Toadfish chorus'), freqMin=c(140, 60, 310, 1200, 150), freqMax=c(6500, 930, 5335, 2600, 3650)), alpha= .85)+
  theme_bw()+
  facet_wrap(factor(site, levels = c('DB01', 'DB02', 'DB03', 'ES01', 'ES02', 'ES03', 'CB01', 'CB02', 'CB03'))~., ncol= 3)+
  ylim(15, 7500)+
  scale_fill_manual(values= c("#4B8320", "#00008B", "purple", "#DB2207","#FFAB38","grey"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size= 16),
        axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        legend.text = element_text(size= 16),
        legend.title= element_text(size=18),
       strip.text= element_text(size= 16))+
  scale_x_datetime(date_breaks = "3 months", date_labels= "%b-%Y", minor_breaks = NULL)+
  geom_rect(data=data.frame(site= factor("ES01")), aes(xmin = as_datetime("2022-06-10"), xmax = as_datetime("2023-10-12"), 
                                           ymin = -Inf, ymax = Inf, fill = ""),
                                           alpha = 0.3, inherit.aes = FALSE, show.legend= "none")+
  geom_rect(data=data.frame(site= factor("ES02")), aes(xmin = as_datetime("2022-06-10"), xmax = as_datetime("2023-10-12"), 
                                           ymin = -Inf, ymax = Inf, fill = ""),
                                           alpha = 0.3, inherit.aes = FALSE, show.legend= "none")+
  geom_rect(data=data.frame(site= factor("ES03")), aes(xmin = as_datetime("2022-06-10"), xmax = as_datetime("2023-10-12"), 
                                           ymin = -Inf, ymax = Inf, fill = ""),
                                           alpha = 0.3, inherit.aes = FALSE, show.legend= "none")+
  geom_rect(data=data.frame(site= factor("CB03")), aes(xmin = as_datetime("2023-11-24"), xmax = as_datetime("2024-05-22"), 
                                           ymin = -Inf, ymax = Inf, fill = ""),
                                           alpha = 0.3, inherit.aes = FALSE, show.legend= "none")


```
#Unknown pulse chorus presence full effort timeseries- inshore at peak diel time
```{r}
#DB01
DB01_location <- matrix(c(-74.82, 38.71), nrow = 1)
DB01500_fullEffort_date_time <- seq(ymd_hms("2022-07-07 00:00:00"), ymd_hms("2024-11-03 23:00:00"), by = "1 hour")

DB01500_fullEffort_nautdusk <- crepuscule(crds = DB01_location, dateTime = DB01500_fullEffort_date_time, solarDep = 12, direction = "dusk", POSIXct.out = TRUE)

DB01500_fullEffort_nautduskDate<- DB01500_fullEffort_nautdusk %>%
  mutate(UTC_date = date(time))%>%
  mutate(nautdusk_UTC_hour = hour(time))

DB01500_fullEffort_nautduskDate <- DB01500_fullEffort_nautduskDate %>%
  group_by(UTC_date, nautdusk_UTC_hour)%>%
  summarize(n = n())
DB01500_fullEffort_nautduskDate <- DB01500_fullEffort_nautduskDate[-c(3)]

#put back as characters so can make date column easier
DB01500_fullEffort_nautduskDate$UTC_date <- as.character(DB01500_fullEffort_nautduskDate$UTC_date)

DB01500_fullEffort_nautduskDate$nautdusk_UTC_hour <- as.character(DB01500_fullEffort_nautduskDate$nautdusk_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
DB01500_fullEffort_nautduskDate$UTC_fixed <- paste(DB01500_fullEffort_nautduskDate$UTC_date, DB01500_fullEffort_nautduskDate$nautdusk_UTC_hour, sep = " ")
DB01500_fullEffort_nautduskDate$UTC_fixed = as.POSIXct(DB01500_fullEffort_nautduskDate$UTC_fixed, format = "%Y-%m-%d %H")

DB01500_fullEffort_nautduskDate$UTC_minus <- DB01500_fullEffort_nautduskDate$UTC_fixed - hours(1)
DB01500_fullEffort_nautduskDate$UTC_plus <- DB01500_fullEffort_nautduskDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
DB01500_fullEffort_nautduskMinus <- DB01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_minus")]
DB01500_fullEffort_nautduskPlus <- DB01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_plus")]

#remove from original for now
DB01500_fullEffort_nautduskDate <- DB01500_fullEffort_nautduskDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(DB01500_fullEffort_nautduskMinus)[3] <- "UTC_fixed"
colnames(DB01500_fullEffort_nautduskPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
DB01500_fullEffort_nautduskDate$UTC_date <- as.Date(DB01500_fullEffort_nautduskDate$UTC_date)

DB01500_fullEffort_nautduskMinus$UTC_date <- as.Date(DB01500_fullEffort_nautduskMinus$UTC_date)
DB01_nautduskMinus <- DB01_OL %>%
  right_join(DB01500_fullEffort_nautduskMinus, join_by(UTC_fixed))

DB01500_fullEffort_nautduskPlus$UTC_date <- as.Date(DB01500_fullEffort_nautduskPlus$UTC_date)
DB01_nautduskPlus <- DB01_OL %>%
  right_join(DB01500_fullEffort_nautduskPlus, join_by(UTC_fixed))

DB01_nautdusk <- DB01_OL %>%
  right_join(DB01500_fullEffort_nautduskDate, join_by(UTC_fixed))

#remove columns not needed for full join
DB01_nautdusk <- DB01_nautdusk[-c(1, 5:8, 10:15, 18)]
colnames(DB01_nautdusk)[9] <- "UTC_date"
DB01_nautdusk$diel <- "naut_dusk"
DB01_nautduskPlus <- DB01_nautduskPlus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(DB01_nautduskPlus)[4] <- "UTC_date"
DB01_nautduskPlus$diel <- "plus"
#DB01_nautduskPlus <- DB01_nautduskPlus[-c(2)]
DB01_nautduskMinus <- DB01_nautduskMinus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(DB01_nautduskMinus)[4] <- "UTC_date"
DB01_nautduskMinus$diel <- "minus"
#DB01_nautduskMinus <- DB01_nautduskMinus[-c(2)]

DB01_nautduskMinusPlus <- DB01_nautduskMinus %>%
  full_join(DB01_nautduskPlus)
DB01_nautdusk_diels <- DB01_nautdusk %>%
  full_join(DB01_nautduskMinusPlus)

DB01_chorusPresence <- DB01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
DB01_nautdusk_diels <- DB01_chorusPresence %>%
  right_join(DB01_nautdusk_diels, join_by(UTC_date))

DB01_nautdusk_diels <- DB01_nautdusk_diels[-c(3:5, 18)]
 
DB01_nautdusk_diels <- DB01_nautdusk_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
DB01_nautdusk_diels <- DB01_nautdusk_diels %>%
  drop_na(X500_chorus)
DB01_nautdusk_diels$site <- "DB01"

DB01pulse_medDiels <- DB01_nautdusk_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
DB01pulse_medDiels <- DB01_chorusPresence %>%
  right_join(DB01pulse_medDiels, join_by(UTC_date))
DB01pulse_medDiels <- DB01pulse_medDiels[-c(3:7)]
colnames(DB01pulse_medDiels)[3] <- "site"

DB01pulse_medDiels <- DB01pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))


DB01pulse_medDiels$dt_ma <- data.table::frollmean(DB01pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
DB01pulse_medDiels$site_label <- "Delaware"

#ES01
ES01_location <- matrix(c(-75.29, 37.69), nrow = 1)
ES01500_fullEffort_date_time  <- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

ES01500_fullEffort_nautdusk <- crepuscule(crds = ES01_location, dateTime = ES01500_fullEffort_date_time, solarDep = 12, direction = "dusk", POSIXct.out = TRUE)

ES01500_fullEffort_nautduskDate<- ES01500_fullEffort_nautdusk %>%
  mutate(UTC_date = date(time))%>%
  mutate(nautdusk_UTC_hour = hour(time))

ES01500_fullEffort_nautduskDate <- ES01500_fullEffort_nautduskDate %>%
  group_by(UTC_date, nautdusk_UTC_hour)%>%
  summarize(n = n())
ES01500_fullEffort_nautduskDate <-ES01500_fullEffort_nautduskDate[-c(3)]

#put back as characters so can make date column easier
ES01500_fullEffort_nautduskDate$UTC_date <- as.character(ES01500_fullEffort_nautduskDate$UTC_date)

ES01500_fullEffort_nautduskDate$nautdusk_UTC_hour <- as.character(ES01500_fullEffort_nautduskDate$nautdusk_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
ES01500_fullEffort_nautduskDate$UTC_fixed <- paste(ES01500_fullEffort_nautduskDate$UTC_date, ES01500_fullEffort_nautduskDate$nautdusk_UTC_hour, sep = " ")
ES01500_fullEffort_nautduskDate$UTC_fixed = as.POSIXct(ES01500_fullEffort_nautduskDate$UTC_fixed, format = "%Y-%m-%d %H")

ES01500_fullEffort_nautduskDate$UTC_minus <- ES01500_fullEffort_nautduskDate$UTC_fixed - hours(1)
ES01500_fullEffort_nautduskDate$UTC_plus <- ES01500_fullEffort_nautduskDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
ES01500_fullEffort_nautduskMinus <- ES01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_minus")]
ES01500_fullEffort_nautduskPlus <- ES01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_plus")]

#remove from original for now
ES01500_fullEffort_nautduskDate <- ES01500_fullEffort_nautduskDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(ES01500_fullEffort_nautduskMinus)[3] <- "UTC_fixed"
colnames(ES01500_fullEffort_nautduskPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
ES01500_fullEffort_nautduskDate$UTC_date <- as.Date(ES01500_fullEffort_nautduskDate$UTC_date)

ES01500_fullEffort_nautduskMinus$UTC_date <- as.Date(ES01500_fullEffort_nautduskMinus$UTC_date)
ES01_nautduskMinus <- ES01_OL %>%
  right_join(ES01500_fullEffort_nautduskMinus, join_by(UTC_fixed))

ES01500_fullEffort_nautduskPlus$UTC_date <- as.Date(ES01500_fullEffort_nautduskPlus$UTC_date)
ES01_nautduskPlus <- ES01_OL %>%
  right_join(ES01500_fullEffort_nautduskPlus, join_by(UTC_fixed))

ES01_nautdusk <- ES01_OL %>%
  right_join(ES01500_fullEffort_nautduskDate, join_by(UTC_fixed))

#remove columns not needed for full join
ES01_nautdusk <- ES01_nautdusk[-c(1, 5:8, 10:15, 18)]
colnames(ES01_nautdusk)[9] <- "UTC_date"
ES01_nautdusk$diel <- "naut_dusk"
ES01_nautduskPlus <-ES01_nautduskPlus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(ES01_nautduskPlus)[4] <- "UTC_date"
ES01_nautduskPlus$diel <- "plus"
ES01_nautduskMinus <- ES01_nautduskMinus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(ES01_nautduskMinus)[4] <- "UTC_date"
ES01_nautduskMinus$diel <- "minus"

ES01_nautduskMinusPlus <- ES01_nautduskMinus %>%
  full_join(ES01_nautduskPlus)
ES01_nautdusk_diels <- ES01_nautdusk %>%
  full_join(ES01_nautduskMinusPlus)

ES01_chorusPresence <- ES01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
ES01_nautdusk_diels <- ES01_chorusPresence %>%
  right_join(ES01_nautdusk_diels, join_by(UTC_date))

ES01_nautdusk_diels <- ES01_nautdusk_diels[-c(3:5, 18)]
 
ES01_nautdusk_diels <- ES01_nautdusk_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
ES01_nautdusk_diels <- ES01_nautdusk_diels %>%
  drop_na(X500_chorus)
ES01_nautdusk_diels$site <- "ES01"

ES01pulse_medDiels <- ES01_nautdusk_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
ES01pulse_medDiels <- ES01_chorusPresence %>%
  right_join(ES01pulse_medDiels, join_by(UTC_date))
ES01pulse_medDiels <- ES01pulse_medDiels[-c(3:7)]
colnames(ES01pulse_medDiels)[3] <- "site"


ES01pulse_medDiels <- ES01pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))

ES01pulse_medDiels$dt_ma <- data.table::frollmean(ES01pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
ES01pulse_medDiels$site_label <- "Eastern"

#CB01
CB01_location <- matrix(c(-75.67, 36.98), nrow = 1)
CB01500_fullEffort_date_time<- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

CB01500_fullEffort_nautdusk <- crepuscule(crds = CB01_location, dateTime = CB01500_fullEffort_date_time, solarDep = 12, direction = "dusk", POSIXct.out = TRUE)

CB01500_fullEffort_nautduskDate<- CB01500_fullEffort_nautdusk %>%
  mutate(UTC_date = date(time))%>%
  mutate(nautdusk_UTC_hour = hour(time))

CB01500_fullEffort_nautduskDate <- CB01500_fullEffort_nautduskDate %>%
  group_by(UTC_date, nautdusk_UTC_hour)%>%
  summarize(n = n())
CB01500_fullEffort_nautduskDate <-CB01500_fullEffort_nautduskDate[-c(3)]

#put back as characters so can make date column easier
CB01500_fullEffort_nautduskDate$UTC_date <- as.character(CB01500_fullEffort_nautduskDate$UTC_date)

CB01500_fullEffort_nautduskDate$nautdusk_UTC_hour <- as.character(CB01500_fullEffort_nautduskDate$nautdusk_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
CB01500_fullEffort_nautduskDate$UTC_fixed <- paste(CB01500_fullEffort_nautduskDate$UTC_date, CB01500_fullEffort_nautduskDate$nautdusk_UTC_hour, sep = " ")
CB01500_fullEffort_nautduskDate$UTC_fixed = as.POSIXct(CB01500_fullEffort_nautduskDate$UTC_fixed, format = "%Y-%m-%d %H")

CB01500_fullEffort_nautduskDate$UTC_minus <- CB01500_fullEffort_nautduskDate$UTC_fixed - hours(1)
CB01500_fullEffort_nautduskDate$UTC_plus <- CB01500_fullEffort_nautduskDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
CB01500_fullEffort_nautduskMinus <- CB01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_minus")]
CB01500_fullEffort_nautduskPlus <- CB01500_fullEffort_nautduskDate[, c("UTC_date", "nautdusk_UTC_hour", "UTC_plus")]

#remove from original for now
CB01500_fullEffort_nautduskDate <- CB01500_fullEffort_nautduskDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(CB01500_fullEffort_nautduskMinus)[3] <- "UTC_fixed"
colnames(CB01500_fullEffort_nautduskPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
CB01500_fullEffort_nautduskDate$UTC_date <- as.Date(CB01500_fullEffort_nautduskDate$UTC_date)

CB01500_fullEffort_nautduskMinus$UTC_date <- as.Date(CB01500_fullEffort_nautduskMinus$UTC_date)
CB01_nautduskMinus <- CB01_OL %>%
  right_join(CB01500_fullEffort_nautduskMinus, join_by(UTC_fixed))

CB01500_fullEffort_nautduskPlus$UTC_date <- as.Date(CB01500_fullEffort_nautduskPlus$UTC_date)
CB01_nautduskPlus <- CB01_OL %>%
  right_join(CB01500_fullEffort_nautduskPlus, join_by(UTC_fixed))

CB01_nautdusk <-CB01_OL %>%
  right_join(CB01500_fullEffort_nautduskDate, join_by(UTC_fixed))

#remove columns not needed for full join
CB01_nautdusk <- CB01_nautdusk[-c(1, 5:8, 10:15, 18)]
colnames(CB01_nautdusk)[9] <- "UTC_date"
CB01_nautdusk$diel <- "naut_dusk"
CB01_nautduskPlus <-CB01_nautduskPlus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(CB01_nautduskPlus)[4] <- "UTC_date"
CB01_nautduskPlus$diel <- "plus"
CB01_nautduskMinus <- CB01_nautduskMinus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(CB01_nautduskMinus)[4] <- "UTC_date"
CB01_nautduskMinus$diel <- "minus"

CB01_nautduskMinusPlus <- CB01_nautduskMinus %>%
  full_join(CB01_nautduskPlus)
CB01_nautdusk_diels <- CB01_nautdusk %>%
  full_join(CB01_nautduskMinusPlus)

CB01_chorusPresence <- CB01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
CB01_nautdusk_diels <- CB01_chorusPresence %>%
  right_join(CB01_nautdusk_diels, join_by(UTC_date))

CB01_nautdusk_diels <- CB01_nautdusk_diels[-c(3:5, 18)]
 
CB01_nautdusk_diels <- CB01_nautdusk_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
CB01_nautdusk_diels <- CB01_nautdusk_diels %>%
  drop_na(X500_chorus)
CB01_nautdusk_diels$site <- "CB01"

CB01pulse_medDiels <- CB01_nautdusk_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
CB01pulse_medDiels <- CB01_chorusPresence %>%
  right_join(CB01pulse_medDiels, join_by(UTC_date))
CB01pulse_medDiels <- CB01pulse_medDiels[-c(3:7)]
colnames(CB01pulse_medDiels)[3] <- "site"

CB01pulse_medDiels <- CB01pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))

CB01pulse_medDiels$dt_ma <- data.table::frollmean(CB01pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
CB01pulse_medDiels$site_label <- "Chesapeake"

#COMBINING AND PLOTTING
ALLpulse_medDiels <- DB01pulse_medDiels %>%
  full_join(ES01pulse_medDiels)%>%
  full_join(CB01pulse_medDiels)
ALLpulse_medDiels$site = factor(ALLpulse_medDiels$site,
                                        levels= c('DB01', 'ES01', 'CB01'),
                                        labels= c('DB01', 'ES01', 'CB01'))
ALLpulse_medDiels$site_label = factor(ALLpulse_medDiels$site_label,
                                        levels= c('Delaware', 'Eastern', 'Chesapeake'),
                                        labels= c('Delaware', 'Eastern', 'Chesapeake'))

# all500_inshoreDiels <- DB01_nautdusk_diels %>%
#   full_join(ES01_nautdusk_diels)%>%
#   full_join(CB01_nautdusk_diels)
# 
# all500_inshoreDiels$site = factor(all500_inshoreDiels$site,
#                                         levels= c('DB01', 'ES01', 'CB01'),
#                                         labels= c('DB01', 'ES01', 'CB01'))

# #regular median (+/- peak hour)
# ggplot(ALLpulse_medDiels, aes(x= UTC, group= year(UTC), y= med_500, group= X500_chorus, color= X500_chorus))+
#   geom_line(linewidth= 0.75, na.rm= TRUE)+
#   theme_bw()+
# #  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
#   xlab("Date")+
#   ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
#   facet_grid(factor(site, levels = c('DB01', 'ES01', 'CB01'))~.,)+
#   scale_color_manual(labels= c("Absent","Present"), values= c("grey75", "#00797F75"))+
#   scale_fill_manual(values= c("grey75", "#00797F75"))+
# #  guides(color= guide_legend(title= "Unknown pulses: chorus presence"))+
# #  ggtitle("+/- 1 hour nautical dusk")+
#   theme(axis.title= element_text(size= 18),
#         axis.text.y= element_text(size= 16),
#         axis.text.x= element_text(size= 16),
#         legend.title= element_text(size= 18),
#         legend.text = element_text(size= 16),
#         plot.title = element_text(size= 20, hjust= 0.5),
#         strip.text= element_text(size= 16))

#rolling avg
inshore_unknownFullEffort <- ggplot(ALLpulse_medDiels, aes(x= UTC, group= year(UTC), y= dt_ma, group= X500_chorus, color= X500_chorus))+
  geom_line(linewidth= 0.75, na.rm= TRUE)+
  theme_bw()+
#  geom_line(data= DB01pulse_medDiels, aes(y= dt_ma), color= "black")+
  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
  xlab("Date")+
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  ylim(75, 145)+
  facet_grid(factor(site_label, levels = c('Delaware', 'Eastern', 'Chesapeake'))~.,)+
  scale_color_manual(labels= c("Absent","Present"), values= c("grey75", "#00797F75"))+
  scale_fill_manual(values= c("grey75", "#00797F75"))+
  guides(color= guide_legend(title= "Unknown pulse: chorus presence"))+
  ggtitle("Inshore +/- 1 hour nautical dusk")+
  theme(axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        axis.text.x= element_text(size= 16),
        legend.title= element_text(size= 18),
        legend.text = element_text(size= 16),
        plot.title = element_text(size= 20, hjust= 0.5),
        strip.text= element_text(size= 11))


plot(inshore_unknownFullEffort)



```
#Unknown pulse chorus presence full effort timeseries- mid-shore at peak diel times
```{r}
#DB02
DB02_location <- matrix(c(-74.47, 38.48), nrow = 1)
DB02500_fullEffort_date_time <- seq(ymd_hms("2022-07-07 00:00:00"), ymd_hms("2024-11-03 23:00:00"), by = "1 hour")

DB02500_fullEffort_sunset <- sunriset(crds = DB02_location, dateTime = DB02500_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

DB02500_fullEffort_sunsetDate<- DB02500_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

DB02500_fullEffort_sunsetDate <- DB02500_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
DB02500_fullEffort_sunsetDate <- DB02500_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
DB02500_fullEffort_sunsetDate$UTC_date <- as.character(DB02500_fullEffort_sunsetDate$UTC_date)

DB02500_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(DB02500_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
DB02500_fullEffort_sunsetDate$UTC_fixed <- paste(DB02500_fullEffort_sunsetDate$UTC_date, DB02500_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
DB02500_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(DB02500_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

DB02500_fullEffort_sunsetDate$UTC_minus <- DB02500_fullEffort_sunsetDate$UTC_fixed - hours(1)
DB02500_fullEffort_sunsetDate$UTC_plus <- DB02500_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
DB02500_fullEffort_sunsetMinus <- DB02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
DB02500_fullEffort_sunsetPlus <- DB02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
DB02500_fullEffort_sunsetDate <- DB02500_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(DB02500_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(DB02500_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
DB02500_fullEffort_sunsetDate$UTC_date <- as.Date(DB02500_fullEffort_sunsetDate$UTC_date)

DB02500_fullEffort_sunsetMinus$UTC_date <- as.Date(DB02500_fullEffort_sunsetMinus$UTC_date)
DB02_sunsetMinus <- DB02_OL %>%
  right_join(DB02500_fullEffort_sunsetMinus, join_by(UTC_fixed))

DB02500_fullEffort_sunsetPlus$UTC_date <- as.Date(DB02500_fullEffort_sunsetPlus$UTC_date)
DB02_sunsetPlus <- DB02_OL %>%
  right_join(DB02500_fullEffort_sunsetPlus, join_by(UTC_fixed))

DB02_sunset <- DB02_OL %>%
  right_join(DB02500_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
DB02_sunset <- DB02_sunset[-c(1, 5:8, 10:15, 18)]
colnames(DB02_sunset)[9] <- "UTC_date"
DB02_sunset$diel <- "sunset"
DB02_sunsetPlus <- DB02_sunsetPlus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(DB02_sunsetPlus)[4] <- "UTC_date"
DB02_sunsetPlus$diel <- "plus"
#DB02_sunsetPlus <- DB02_sunsetPlus[-c(2)]
DB02_sunsetMinus <- DB02_sunsetMinus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(DB02_sunsetMinus)[4] <- "UTC_date"
DB02_sunsetMinus$diel <- "minus"
#DB02_sunsetMinus <- DB02_sunsetMinus[-c(2)]

DB02_sunsetMinusPlus <- DB02_sunsetMinus %>%
  full_join(DB02_sunsetPlus)
DB02_sunset_diels <- DB02_sunset %>%
  full_join(DB02_sunsetMinusPlus)

DB02_chorusPresence <- DB02_chorusPresence %>%
  mutate(UTC_date = date(UTC))
DB02_sunset_diels <- DB02_chorusPresence %>%
  right_join(DB02_sunset_diels, join_by(UTC_date))

DB02_sunset_diels <- DB02_sunset_diels[-c(3:5, 18)]
 
DB02_sunset_diels <- DB02_sunset_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
DB02_sunset_diels <- DB02_sunset_diels %>%
  drop_na(X500_chorus)
DB02_sunset_diels$site <- "DB02"

DB02pulse_medDiels <- DB02_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
DB02pulse_medDiels <- DB02_chorusPresence %>%
  right_join(DB02pulse_medDiels, join_by(UTC_date))
DB02pulse_medDiels <- DB02pulse_medDiels[-c(3:7)]
colnames(DB02pulse_medDiels)[3] <- "site"

DB02pulse_medDiels <- DB02pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))


DB02pulse_medDiels$dt_ma <- data.table::frollmean(DB02pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
DB02pulse_medDiels$site_label <- "Delaware"


#ES02
ES02_location <- matrix(c(-74.83, 37.68), nrow = 1)
ES02500_fullEffort_date_time  <- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

ES02500_fullEffort_sunset <- sunriset(crds = ES02_location, dateTime = ES02500_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

ES02500_fullEffort_sunsetDate<- ES02500_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

ES02500_fullEffort_sunsetDate <- ES02500_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
ES02500_fullEffort_sunsetDate <-ES02500_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
ES02500_fullEffort_sunsetDate$UTC_date <- as.character(ES02500_fullEffort_sunsetDate$UTC_date)

ES02500_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(ES02500_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
ES02500_fullEffort_sunsetDate$UTC_fixed <- paste(ES02500_fullEffort_sunsetDate$UTC_date, ES02500_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
ES02500_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(ES02500_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

ES02500_fullEffort_sunsetDate$UTC_minus <- ES02500_fullEffort_sunsetDate$UTC_fixed - hours(1)
ES02500_fullEffort_sunsetDate$UTC_plus <- ES02500_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
ES02500_fullEffort_sunsetMinus <- ES02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
ES02500_fullEffort_sunsetPlus <- ES02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
ES02500_fullEffort_sunsetDate <- ES02500_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(ES02500_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(ES02500_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
ES02500_fullEffort_sunsetDate$UTC_date <- as.Date(ES02500_fullEffort_sunsetDate$UTC_date)

ES02500_fullEffort_sunsetMinus$UTC_date <- as.Date(ES02500_fullEffort_sunsetMinus$UTC_date)
ES02_sunsetMinus <- ES02_OL %>%
  right_join(ES02500_fullEffort_sunsetMinus, join_by(UTC_fixed))

ES02500_fullEffort_sunsetPlus$UTC_date <- as.Date(ES02500_fullEffort_sunsetPlus$UTC_date)
ES02_sunsetPlus <- ES02_OL %>%
  right_join(ES02500_fullEffort_sunsetPlus, join_by(UTC_fixed))

ES02_sunset <- ES02_OL %>%
  right_join(ES02500_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
ES02_sunset <- ES02_sunset[-c(1, 5:8, 10:15, 18)]
colnames(ES02_sunset)[9] <- "UTC_date"
ES02_sunset$diel <- "sunset"
ES02_sunsetPlus <-ES02_sunsetPlus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(ES02_sunsetPlus)[4] <- "UTC_date"
ES02_sunsetPlus$diel <- "plus"
ES02_sunsetMinus <- ES02_sunsetMinus[-c(1:8, 10:14, 16, 18:20, 22)]
colnames(ES02_sunsetMinus)[4] <- "UTC_date"
ES02_sunsetMinus$diel <- "minus"

ES02_sunsetMinusPlus <- ES02_sunsetMinus %>%
  full_join(ES02_sunsetPlus)
ES02_sunset_diels <- ES02_sunset %>%
  full_join(ES02_sunsetMinusPlus)

ES02_chorusPresence <- ES02_chorusPresence %>%
  mutate(UTC_date = date(UTC))
ES02_sunset_diels <- ES02_chorusPresence %>%
  right_join(ES02_sunset_diels, join_by(UTC_date))

ES02_sunset_diels <- ES02_sunset_diels[-c(3:5, 18)]
 
ES02_sunset_diels <- ES02_sunset_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
ES02_sunset_diels <- ES02_sunset_diels %>%
  drop_na(X500_chorus)
ES02_sunset_diels$site <- "ES02"

ES02pulse_medDiels <- ES02_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
ES02pulse_medDiels <- ES02_chorusPresence %>%
  right_join(ES02pulse_medDiels, join_by(UTC_date))
ES02pulse_medDiels <- ES02pulse_medDiels[-c(3:7)]
colnames(ES02pulse_medDiels)[3] <- "site"


ES02pulse_medDiels <- ES02pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))

ES02pulse_medDiels$dt_ma <- data.table::frollmean(ES02pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
ES02pulse_medDiels$site_label <- "Eastern"

#CB02
CB02_location <- matrix(c(-75.22, 36.98), nrow = 1)
CB02500_fullEffort_date_time<- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

CB02500_fullEffort_sunset <- sunriset(crds = CB02_location, dateTime = CB02500_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

CB02500_fullEffort_sunsetDate<- CB02500_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

CB02500_fullEffort_sunsetDate <- CB02500_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
CB02500_fullEffort_sunsetDate <-CB02500_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
CB02500_fullEffort_sunsetDate$UTC_date <- as.character(CB02500_fullEffort_sunsetDate$UTC_date)

CB02500_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(CB02500_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
CB02500_fullEffort_sunsetDate$UTC_fixed <- paste(CB02500_fullEffort_sunsetDate$UTC_date, CB02500_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
CB02500_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(CB02500_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

CB02500_fullEffort_sunsetDate$UTC_minus <- CB02500_fullEffort_sunsetDate$UTC_fixed - hours(1)
CB02500_fullEffort_sunsetDate$UTC_plus <- CB02500_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
CB02500_fullEffort_sunsetMinus <- CB02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
CB02500_fullEffort_sunsetPlus <- CB02500_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
CB02500_fullEffort_sunsetDate <- CB02500_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(CB02500_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(CB02500_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
CB02500_fullEffort_sunsetDate$UTC_date <- as.Date(CB02500_fullEffort_sunsetDate$UTC_date)

CB02500_fullEffort_sunsetMinus$UTC_date <- as.Date(CB02500_fullEffort_sunsetMinus$UTC_date)
CB02_sunsetMinus <- CB02_OL %>%
  right_join(CB02500_fullEffort_sunsetMinus, join_by(UTC_fixed))

CB02500_fullEffort_sunsetPlus$UTC_date <- as.Date(CB02500_fullEffort_sunsetPlus$UTC_date)
CB02_sunsetPlus <- CB02_OL %>%
  right_join(CB02500_fullEffort_sunsetPlus, join_by(UTC_fixed))

CB02_sunset <-CB02_OL %>%
  right_join(CB02500_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
CB02_sunset <- CB02_sunset[-c(1, 5:10, 12:17)]
colnames(CB02_sunset)[9] <- "UTC_date"
CB02_sunset$diel <- "sunset"
CB02_sunsetPlus <-CB02_sunsetPlus[-c(1:10, 12:16, 18, 20:21, 23)]
colnames(CB02_sunsetPlus)[4] <- "UTC_date"
CB02_sunsetPlus$diel <- "plus"
CB02_sunsetMinus <- CB02_sunsetMinus[-c(1:10, 12:16, 18, 20:21, 23)]
colnames(CB02_sunsetMinus)[4] <- "UTC_date"
CB02_sunsetMinus$diel <- "minus"

CB02_sunsetMinusPlus <- CB02_sunsetMinus %>%
  full_join(CB02_sunsetPlus)
CB02_sunset_diels <- CB02_sunset %>%
  full_join(CB02_sunsetMinusPlus)

CB02_chorusPresence <- CB02_chorusPresence %>%
  mutate(UTC_date = date(UTC))
CB02_sunset_diels <- CB02_chorusPresence %>%
  right_join(CB02_sunset_diels, join_by(UTC_date))

CB02_sunset_diels <- CB02_sunset_diels[-c(3:5, 18)]
 
CB02_sunset_diels <- CB02_sunset_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
CB02_sunset_diels <- CB02_sunset_diels %>%
  drop_na(X500_chorus)
CB02_sunset_diels$site <- "CB02"

CB02pulse_medDiels <- CB02_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
CB02pulse_medDiels <- CB02_chorusPresence %>%
  right_join(CB02pulse_medDiels, join_by(UTC_date))
CB02pulse_medDiels <- CB02pulse_medDiels[-c(3:7)]
colnames(CB02pulse_medDiels)[3] <- "site"

CB02pulse_medDiels <- CB02pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))

CB02pulse_medDiels$dt_ma <- data.table::frollmean(CB02pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
CB02pulse_medDiels$site_label <- "Chesapeake 1"



#CB03
CB03_location <- matrix(c(-75.31, 36.51), nrow = 1)
CB03500_fullEffort_date_time <- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 23:00:00"), by = "1 hour")

CB03500_fullEffort_civdusk <- crepuscule(crds = CB03_location, dateTime = CB03500_fullEffort_date_time, solarDep = 6, direction = "dusk", POSIXct.out = TRUE)

CB03500_fullEffort_civduskDate<- CB03500_fullEffort_civdusk %>%
  mutate(UTC_date = date(time))%>%
  mutate(civdusk_UTC_hour = hour(time))

CB03500_fullEffort_civduskDate <- CB03500_fullEffort_civduskDate %>%
  group_by(UTC_date, civdusk_UTC_hour)%>%
  summarize(n = n())
CB03500_fullEffort_civduskDate <- CB03500_fullEffort_civduskDate[-c(3)]

#put back as characters so can make date column easier
CB03500_fullEffort_civduskDate$UTC_date <- as.character(CB03500_fullEffort_civduskDate$UTC_date)

CB03500_fullEffort_civduskDate$civdusk_UTC_hour <- as.character(CB03500_fullEffort_civduskDate$civdusk_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
CB03500_fullEffort_civduskDate$UTC_fixed <- paste(CB03500_fullEffort_civduskDate$UTC_date, CB03500_fullEffort_civduskDate$civdusk_UTC_hour, sep = " ")
CB03500_fullEffort_civduskDate$UTC_fixed = as.POSIXct(CB03500_fullEffort_civduskDate$UTC_fixed, format = "%Y-%m-%d %H")

CB03500_fullEffort_civduskDate$UTC_minus <- CB03500_fullEffort_civduskDate$UTC_fixed - hours(1)
CB03500_fullEffort_civduskDate$UTC_plus <- CB03500_fullEffort_civduskDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
CB03500_fullEffort_civduskMinus <- CB03500_fullEffort_civduskDate[, c("UTC_date", "civdusk_UTC_hour", "UTC_minus")]
CB03500_fullEffort_civduskPlus <- CB03500_fullEffort_civduskDate[, c("UTC_date", "civdusk_UTC_hour", "UTC_plus")]

#remove from original for now
CB03500_fullEffort_civduskDate <- CB03500_fullEffort_civduskDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(CB03500_fullEffort_civduskMinus)[3] <- "UTC_fixed"
colnames(CB03500_fullEffort_civduskPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
CB03500_fullEffort_civduskDate$UTC_date <- as.Date(CB03500_fullEffort_civduskDate$UTC_date)

CB03500_fullEffort_civduskMinus$UTC_date <- as.Date(CB03500_fullEffort_civduskMinus$UTC_date)
CB03_civduskMinus <- CB03_OL %>%
  right_join(CB03500_fullEffort_civduskMinus, join_by(UTC_fixed))

CB03500_fullEffort_civduskPlus$UTC_date <- as.Date(CB03500_fullEffort_civduskPlus$UTC_date)
CB03_civduskPlus <- CB03_OL %>%
  right_join(CB03500_fullEffort_civduskPlus, join_by(UTC_fixed))

CB03_civdusk <- CB03_OL %>%
  right_join(CB03500_fullEffort_civduskDate, join_by(UTC_fixed))

#remove columns not needed for full join
CB03_civdusk <- CB03_civdusk[-c(1, 5:9, 11:16)]
colnames(CB03_civdusk)[9] <- "UTC_date"
CB03_civdusk$diel <- "civ_dusk"
CB03_civduskPlus <- CB03_civduskPlus[-c(1:9, 11:16, 19:20, 22)]
colnames(CB03_civduskPlus)[4] <- "UTC_date"
CB03_civduskPlus$diel <- "plus"
#CB03_civduskPlus <- CB03_civduskPlus[-c(2)]
CB03_civduskMinus <- CB03_civduskMinus[-c(1:9, 11:16, 19:20, 22)]
colnames(CB03_civduskMinus)[4] <- "UTC_date"
CB03_civduskMinus$diel <- "minus"
#CB03_civduskMinus <- CB03_civduskMinus[-c(2)]

CB03_civduskMinusPlus <- CB03_civduskMinus %>%
  full_join(CB03_civduskPlus)
CB03_civdusk_diels <- CB03_civdusk %>%
  full_join(CB03_civduskMinusPlus)

CB03_chorusPresence <- CB03_chorusPresence %>%
  mutate(UTC_date = date(UTC))
CB03_civdusk_diels <- CB03_chorusPresence %>%
  right_join(CB03_civdusk_diels, join_by(UTC_date))

CB03_civdusk_diels <- CB03_civdusk_diels[-c(3:5)]
 
CB03_civdusk_diels <- CB03_civdusk_diels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
CB03_civdusk_diels <- CB03_civdusk_diels %>%
  drop_na(X500_chorus)
CB03_civdusk_diels$site <- "CB03"

CB03pulse_medDiels <- CB03_civdusk_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_500 = median(OL_500, na.rm=TRUE))
CB03pulse_medDiels <- CB03_chorusPresence %>%
  right_join(CB03pulse_medDiels, join_by(UTC_date))
CB03pulse_medDiels <- CB03pulse_medDiels[-c(3:7)]
colnames(CB03pulse_medDiels)[3] <- "site"

CB03pulse_medDiels <- CB03pulse_medDiels %>%
dplyr::mutate(X500_chorus = factor(X500_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))


CB03pulse_medDiels$dt_ma <- data.table::frollmean(CB03pulse_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
CB03pulse_medDiels$site_label <- "Chesapeake 2"


#COMBINING AND PLOTTING
ALLpulse_medDiels <- DB02pulse_medDiels %>%
  full_join(ES02pulse_medDiels)%>%
  full_join(CB02pulse_medDiels) #%>%
# full_join(CB03pulse_medDiels)
# ALLpulse_medDiels$site = factor(ALLpulse_medDiels$site,
#                                         levels= c('DB02', 'ES02', 'CB02', 'CB03'),
#                                         labels= c('DB02', 'ES02', 'CB02', 'CB03'))
ALLpulse_medDiels$site = factor(ALLpulse_medDiels$site,
                                        levels= c('DB02', 'ES02', 'CB02'),
                                        labels= c('DB02', 'ES02', 'CB02'))
ALLpulse_medDiels$site_label = factor(ALLpulse_medDiels$site_label,
                                        levels= c('Delaware', 'Eastern', 'Chesapeake 1'),
                                        labels= c('Delaware', 'Eastern', 'Chesapeake 1'))

# all500_midshoreDiels <- DB02_sunset_diels %>%
#   full_join(ES02_sunset_diels)%>%
#   full_join(CB02_sunset_diels)

# all500_midshoreDiels$site = factor(all500_midshoreDiels$site,
#                                         levels= c('DB02', 'ES02', 'CB02'),
#                                         labels= c('DB02', 'ES02', 'CB02'))

# #regular median (+/- peak hour)
# ggplot(CB03pulse_medDiels, aes(x= UTC, group= year(UTC), y= med_500, group= X500_chorus, color= X500_chorus))+
#   geom_line(linewidth= 0.75, na.rm= TRUE)+
#   theme_bw()+
# #  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
#   xlab("Date")+
#   ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
#   facet_grid(factor(site_label, levels = c('Chesapeake 2'))~.,)+
#   scale_color_manual(labels= c("Absent","Present"), values= c("grey75", "#00797F75"))+
#   scale_fill_manual(values= c("grey75", "#00797F75"))+
# #  guides(color= guide_legend(title= "Unknown pulses: chorus presence"))+
#   ggtitle("Midshore: +/- 1 hour civ dusk")+
#   theme(axis.title= element_text(size= 18),
#         axis.text.y= element_text(size= 16),
#         axis.text.x= element_text(size= 16),
#         legend.title= element_text(size= 18),
#         legend.text = element_text(size= 16),
#         plot.title = element_text(size= 20, hjust= 0.5),
#         strip.text= element_text(size= 12))

#rolling avg
midshore_unknownFullEffort <- ggplot(ALLpulse_medDiels, aes(x= UTC, group= year(UTC), y= dt_ma, group= X500_chorus, color= X500_chorus))+
  geom_line(linewidth= 0.75, na.rm= TRUE)+
  theme_bw()+
#  geom_line(data= DB02pulse_medDiels, aes(y= dt_ma), color= "black")+
  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
  xlab("Date")+
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
    ylim(75, 145)+
  facet_grid(factor(site_label, levels = c('Delaware', 'Eastern', 'Chesapeake 1'))~.,)+
  scale_color_manual(labels= c("Absent","Present"), values= c("grey75", "#00797F75"))+
  scale_fill_manual(values= c("grey75", "#00797F75"))+
  guides(color= guide_legend(title= "Unknown pulse: chorus presence"))+
  ggtitle("Midshore +/- 1 hour sunset ")+
  theme(axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        axis.text.x= element_text(size= 16),
        legend.title= element_text(size= 18),
        legend.text = element_text(size= 16),
        plot.title = element_text(size= 20, hjust= 0.5),
        strip.text= element_text(size= 11))

#CB03
CB03_unknownFullEffort <- ggplot(CB03pulse_medDiels, aes(x= UTC, group= year(UTC), y= dt_ma, group= X500_chorus, color= X500_chorus))+
  geom_line(linewidth= 0.75, na.rm= TRUE)+
  theme_bw()+
  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
  xlab("Date")+
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
    ylim(75, 145)+
    facet_grid(factor(site_label, levels = c('Chesapeake 2'))~.,)+
  scale_color_manual(labels= c("Absent","Present"), values= c("grey75", "#00797F75"))+
  scale_fill_manual(values= c("grey75", "#00797F75"))+
  guides(color= guide_legend(title= "Unknown pulse: chorus presence"))+
  ggtitle("Midshore +/- 1 hour civil dusk ")+
  theme(axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        axis.text.x= element_text(size= 16),
        legend.title= element_text(size= 18),
        legend.text = element_text(size= 16),
        plot.title = element_text(size= 20, hjust= 0.5),
        strip.text= element_text(size= 12))
plot(CB03_unknownFullEffort)

unknown_fullEffortPlot <- inshore_unknownFullEffort/midshore_unknownFullEffort/CB03_unknownFullEffort +plot_layout(guides = "collect", axis_titles = "collect", axes= "collect")

plot(unknown_fullEffortPlot)
ggsave(here("figs", "unknown_fullEffortPlot.png"), unknown_fullEffortPlot, width= 16, height=14, dpi= 600)

```
#Cusk eel chorus presence full effort timeseries- inshore at peak diel time
```{r}
#DB01
DB01_location <- matrix(c(-74.82, 38.71), nrow = 1)
DB01_fullEffort_date_time <- seq(ymd_hms("2022-07-07 00:00:00"), ymd_hms("2024-11-04 23:00:00"), by = "1 hour")

DB01_fullEffort_sunset <- sunriset(crds = DB01_location, dateTime = DB01_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

DB01_fullEffort_sunsetDate<- DB01_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

DB01_fullEffort_sunsetDate <- DB01_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
DB01_fullEffort_sunsetDate <- DB01_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
DB01_fullEffort_sunsetDate$UTC_date <- as.character(DB01_fullEffort_sunsetDate$UTC_date)

DB01_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(DB01_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
DB01_fullEffort_sunsetDate$UTC_fixed <- paste(DB01_fullEffort_sunsetDate$UTC_date, DB01_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
DB01_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(DB01_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

DB01_fullEffort_sunsetDate$UTC_minus <- DB01_fullEffort_sunsetDate$UTC_fixed - hours(1)
DB01_fullEffort_sunsetDate$UTC_plus <- DB01_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
DB01_fullEffort_sunsetMinus <- DB01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
DB01_fullEffort_sunsetPlus <- DB01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
DB01_fullEffort_sunsetDate <- DB01_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(DB01_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(DB01_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
DB01_fullEffort_sunsetDate$UTC_date <- as.Date(DB01_fullEffort_sunsetDate$UTC_date)

DB01_fullEffort_sunsetMinus$UTC_date <- as.Date(DB01_fullEffort_sunsetMinus$UTC_date)
DB01_sunsetMinus <- DB01_OL %>%
  right_join(DB01_fullEffort_sunsetMinus, join_by(UTC_fixed))

DB01_fullEffort_sunsetPlus$UTC_date <- as.Date(DB01_fullEffort_sunsetPlus$UTC_date)
DB01_sunsetPlus <- DB01_OL %>%
  right_join(DB01_fullEffort_sunsetPlus, join_by(UTC_fixed))

DB01_sunset <- DB01_OL %>%
  right_join(DB01_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
DB01_sunset <- DB01_sunset[-c(1, 5:10, 12:15, 18)]
colnames(DB01_sunset)[9] <- "UTC_date"
DB01_sunset$diel <- "sunset"
DB01_sunsetPlus <- DB01_sunsetPlus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(DB01_sunsetPlus)[4] <- "UTC_date"
DB01_sunsetPlus$diel <- "plus"
DB01_sunsetMinus <- DB01_sunsetMinus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(DB01_sunsetMinus)[4] <- "UTC_date"
DB01_sunsetMinus$diel <- "minus"

DB01_sunsetMinusPlus <- DB01_sunsetMinus %>%
  full_join(DB01_sunsetPlus)
DB01_sunset_diels <- DB01_sunset %>%
  full_join(DB01_sunsetMinusPlus)

DB01_chorusPresence <- DB01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
DB01_sunset_diels <- DB01_chorusPresence %>%
  right_join(DB01_sunset_diels, join_by(UTC_date))

DB01_sunset_diels <- DB01_sunset_diels[-c(2:3, 5, 18)]
 
DB01_sunset_diels <- DB01_sunset_diels %>%
dplyr::mutate(cusk_chorus = factor(cusk_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
DB01_sunset_diels <- DB01_sunset_diels %>%
  drop_na(cusk_chorus)
DB01_sunset_diels$site <- "DB01"

DB01cusk_medDiels <- DB01_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_2000 = median(OL_2000, na.rm=TRUE))
DB01cusk_medDiels <- DB01_chorusPresence %>%
  right_join(DB01cusk_medDiels, join_by(UTC_date))
DB01cusk_medDiels <- DB01cusk_medDiels[-c(2,3,5:7)]
colnames(DB01cusk_medDiels)[3] <- "site"

DB01cusk_medDiels$dt_ma <- data.table::frollmean(DB01cusk_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
DB01cusk_medDiels$site_label <- "Delaware"


#ES01
ES01_location <- matrix(c(-75.29, 37.69), nrow = 1)
ES01_fullEffort_date_time  <- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

ES01_fullEffort_sunset <- sunriset(crds = ES01_location, dateTime = ES01_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

ES01_fullEffort_sunsetDate<- ES01_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

ES01_fullEffort_sunsetDate <- ES01_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
ES01_fullEffort_sunsetDate <- ES01_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
ES01_fullEffort_sunsetDate$UTC_date <- as.character(ES01_fullEffort_sunsetDate$UTC_date)

ES01_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(ES01_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
ES01_fullEffort_sunsetDate$UTC_fixed <- paste(ES01_fullEffort_sunsetDate$UTC_date, ES01_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
ES01_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(ES01_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

ES01_fullEffort_sunsetDate$UTC_minus <- ES01_fullEffort_sunsetDate$UTC_fixed - hours(1)
ES01_fullEffort_sunsetDate$UTC_plus <- ES01_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
ES01_fullEffort_sunsetMinus <- ES01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
ES01_fullEffort_sunsetPlus <- ES01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
ES01_fullEffort_sunsetDate <- ES01_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(ES01_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(ES01_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
ES01_fullEffort_sunsetDate$UTC_date <- as.Date(ES01_fullEffort_sunsetDate$UTC_date)

ES01_fullEffort_sunsetMinus$UTC_date <- as.Date(ES01_fullEffort_sunsetMinus$UTC_date)
ES01_sunsetMinus <- ES01_OL %>%
  right_join(ES01_fullEffort_sunsetMinus, join_by(UTC_fixed))

ES01_fullEffort_sunsetPlus$UTC_date <- as.Date(ES01_fullEffort_sunsetPlus$UTC_date)
ES01_sunsetPlus <- ES01_OL %>%
  right_join(ES01_fullEffort_sunsetPlus, join_by(UTC_fixed))

ES01_sunset <- ES01_OL %>%
  right_join(ES01_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
ES01_sunset <- ES01_sunset[-c(1, 5:10, 12:15, 18)]
colnames(ES01_sunset)[9] <- "UTC_date"
ES01_sunset$diel <- "sunset"
ES01_sunsetPlus <- ES01_sunsetPlus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(ES01_sunsetPlus)[4] <- "UTC_date"
ES01_sunsetPlus$diel <- "plus"
ES01_sunsetMinus <- ES01_sunsetMinus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(ES01_sunsetMinus)[4] <- "UTC_date"
ES01_sunsetMinus$diel <- "minus"

ES01_sunsetMinusPlus <- ES01_sunsetMinus %>%
  full_join(ES01_sunsetPlus)
ES01_sunset_diels <- ES01_sunset %>%
  full_join(ES01_sunsetMinusPlus)

ES01_chorusPresence <- ES01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
ES01_sunset_diels <- ES01_chorusPresence %>%
  right_join(ES01_sunset_diels, join_by(UTC_date))

ES01_sunset_diels <- ES01_sunset_diels[-c(2:3, 5, 18)]
 
ES01_sunset_diels <- ES01_sunset_diels %>%
dplyr::mutate(cusk_chorus = factor(cusk_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
ES01_sunset_diels <- ES01_sunset_diels %>%
  drop_na(cusk_chorus)
ES01_sunset_diels$site <- "ES01"

ES01cusk_medDiels <- ES01_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_2000 = median(OL_2000, na.rm=TRUE))
ES01cusk_medDiels <- ES01_chorusPresence %>%
  right_join(ES01cusk_medDiels, join_by(UTC_date))
ES01cusk_medDiels <- ES01cusk_medDiels[-c(2,3,5:7)]
colnames(ES01cusk_medDiels)[3] <- "site"
ES01cusk_medDiels$dt_ma <- data.table::frollmean(ES01cusk_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
ES01cusk_medDiels$site_label <- "Eastern"

#CB01
CB01_location <- matrix(c(-75.67, 36.98), nrow = 1)
CB01_fullEffort_date_time  <- seq(ymd_hms("2022-06-10 00:00:00"), ymd_hms("2024-11-08 16:00:00"), by = "1 hour")

CB01_fullEffort_sunset <- sunriset(crds = CB01_location, dateTime = CB01_fullEffort_date_time, direction = "sunset", POSIXct.out = TRUE)

CB01_fullEffort_sunsetDate<- CB01_fullEffort_sunset %>%
  mutate(UTC_date = date(time))%>%
  mutate(sunset_UTC_hour = hour(time))

CB01_fullEffort_sunsetDate <- CB01_fullEffort_sunsetDate %>%
  group_by(UTC_date, sunset_UTC_hour)%>%
  summarize(n = n())
CB01_fullEffort_sunsetDate <- CB01_fullEffort_sunsetDate[-c(3)]

#put back as characters so can make date column easier
CB01_fullEffort_sunsetDate$UTC_date <- as.character(CB01_fullEffort_sunsetDate$UTC_date)

CB01_fullEffort_sunsetDate$sunset_UTC_hour <- as.character(CB01_fullEffort_sunsetDate$sunset_UTC_hour)

#make new columns combining date and 3 hours- should have 3 data points per day (with overlap on days if around midnight)- 
CB01_fullEffort_sunsetDate$UTC_fixed <- paste(CB01_fullEffort_sunsetDate$UTC_date, CB01_fullEffort_sunsetDate$sunset_UTC_hour, sep = " ")
CB01_fullEffort_sunsetDate$UTC_fixed = as.POSIXct(CB01_fullEffort_sunsetDate$UTC_fixed, format = "%Y-%m-%d %H")

CB01_fullEffort_sunsetDate$UTC_minus <- CB01_fullEffort_sunsetDate$UTC_fixed - hours(1)
CB01_fullEffort_sunsetDate$UTC_plus <- CB01_fullEffort_sunsetDate$UTC_fixed + hours(1)

#this works but hard to then join with OL data, so separate out and then join again after they are all matched
CB01_fullEffort_sunsetMinus <- CB01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_minus")]
CB01_fullEffort_sunsetPlus <- CB01_fullEffort_sunsetDate[, c("UTC_date", "sunset_UTC_hour", "UTC_plus")]

#remove from original for now
CB01_fullEffort_sunsetDate <- CB01_fullEffort_sunsetDate[-c(4:5)]

#have to rename minus/plus columns to 'UTC_fixed' so it can join with the chorus presence and OL files
colnames(CB01_fullEffort_sunsetMinus)[3] <- "UTC_fixed"
colnames(CB01_fullEffort_sunsetPlus)[3] <- "UTC_fixed"

#now join each date dataframe individually
CB01_fullEffort_sunsetDate$UTC_date <- as.Date(CB01_fullEffort_sunsetDate$UTC_date)

CB01_fullEffort_sunsetMinus$UTC_date <- as.Date(CB01_fullEffort_sunsetMinus$UTC_date)
CB01_sunsetMinus <- CB01_OL %>%
  right_join(CB01_fullEffort_sunsetMinus, join_by(UTC_fixed))

CB01_fullEffort_sunsetPlus$UTC_date <- as.Date(CB01_fullEffort_sunsetPlus$UTC_date)
CB01_sunsetPlus <- CB01_OL %>%
  right_join(CB01_fullEffort_sunsetPlus, join_by(UTC_fixed))

CB01_sunset <- CB01_OL %>%
  right_join(CB01_fullEffort_sunsetDate, join_by(UTC_fixed))

#remove columns not needed for full join
CB01_sunset <- CB01_sunset[-c(1, 5:10, 12:15, 18)]
colnames(CB01_sunset)[9] <- "UTC_date"
CB01_sunset$diel <- "sunset"
CB01_sunsetPlus <- CB01_sunsetPlus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(CB01_sunsetPlus)[4] <- "UTC_date"
CB01_sunsetPlus$diel <- "plus"
CB01_sunsetMinus <- CB01_sunsetMinus[-c(1:10, 12:14, 16, 18:20, 22)]
colnames(CB01_sunsetMinus)[4] <- "UTC_date"
CB01_sunsetMinus$diel <- "minus"

CB01_sunsetMinusPlus <- CB01_sunsetMinus %>%
  full_join(CB01_sunsetPlus)
CB01_sunset_diels <- CB01_sunset %>%
  full_join(CB01_sunsetMinusPlus)

CB01_chorusPresence <- CB01_chorusPresence %>%
  mutate(UTC_date = date(UTC))
CB01_sunset_diels <- CB01_chorusPresence %>%
  right_join(CB01_sunset_diels, join_by(UTC_date))

CB01_sunset_diels <- CB01_sunset_diels[-c(2:3, 5, 18)]
 
CB01_sunset_diels <- CB01_sunset_diels %>%
dplyr::mutate(cusk_chorus = factor(cusk_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))
CB01_sunset_diels <- CB01_sunset_diels %>%
  drop_na(cusk_chorus)
CB01_sunset_diels$site <- "CB01"


CB01cusk_medDiels <- CB01_sunset_diels %>%
  group_by(UTC_date, site) %>%
  dplyr::summarize(med_2000 = median(OL_2000, na.rm=TRUE))
CB01cusk_medDiels <- CB01_chorusPresence %>%
  right_join(CB01cusk_medDiels, join_by(UTC_date))
CB01cusk_medDiels <- CB01cusk_medDiels[-c(2,3,5:7)]
colnames(CB01cusk_medDiels)[3] <- "site"
CB01cusk_medDiels$dt_ma <- data.table::frollmean(CB01cusk_medDiels[, 4], n = 3, align = "right", fill = NA, algo = "fast")
CB01cusk_medDiels$site_label <- "Chesapeake"

#COMBINING AND PLOTTING
ALLcusk_medDiels <- DB01cusk_medDiels %>%
  full_join(ES01cusk_medDiels)%>%
  full_join(CB01cusk_medDiels)
ALLcusk_medDiels$site = factor(ALLcusk_medDiels$site,
                                        levels= c('DB01', 'ES01', 'CB01'),
                                        labels= c('DB01', 'ES01', 'CB01'))
ALLcusk_medDiels <- ALLcusk_medDiels %>%
dplyr::mutate(cusk_chorus = factor(cusk_chorus,
                                    levels = c(0, 1),
                                    labels = c("Absent", "Present")))

# allCusk_inshoreDiels <- DB01_sunset_diels %>%
#   full_join(ES01_sunset_diels)%>%
#   full_join(CB01_sunset_diels)
# 
# allCusk_inshoreDiels$site = factor(allCusk_inshoreDiels$site,
#                                         levels= c('DB01', 'ES01', 'CB01'),
#                                         labels= c('DB01', 'ES01', 'CB01'))
ALLcusk_medDiels$site_label = factor(ALLcusk_medDiels$site_label,
                                        levels= c('Delaware', 'Eastern', 'Chesapeake'),
                                        labels= c('Delaware', 'Eastern', 'Chesapeake'))


cuskFullEffort <- ggplot(ALLcusk_medDiels, aes(x= UTC, group= year(UTC), y= dt_ma, group= cusk_chorus, color= cusk_chorus))+
  geom_line(linewidth= 0.75, na.rm= TRUE)+
  theme_bw()+
  scale_x_datetime(date_breaks = "3 months", date_labels= "%b %Y", minor_breaks = NULL)+
  xlab("Date")+
  ylab(expression(paste('Median 2000Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  ylim(75, 145)+
  facet_grid(factor(site_label, levels = c('Delaware', 'Eastern', 'Chesapeake'))~.,)+
  scale_color_manual(labels= c("Absent","Present"), values= c("grey", "#00308795"))+
  scale_fill_manual(values= c("grey", "#00308795"))+
  guides(color= guide_legend(title= "Cusk eel: chorus presence"))+
  ggtitle("Inshore +/- 1 hour sunset")+
  theme(axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        axis.text.x= element_text(size= 16),
        legend.title= element_text(size= 18),
        legend.text = element_text(size= 16),
        plot.title = element_text(size= 20, hjust= 0.5),
        strip.text= element_text(size= 14))

plot(cuskFullEffort)
ggsave(here("figs", "cuskFullEffort.png"), cuskFullEffort, width= 16, height=14, dpi= 600)

```
#Diel plot- using 15minute-level threshold data
```{r}
#Inshore unknown pulse####
DB01_unknownPulse_min <- read.csv(here("data/DB01_unknownPulse_minData.csv"))
DB01_unknownPulse_min$UTC <- as.POSIXct(DB01_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB01_unknownPulse_minOL <- createOctaveLevel(DB01_unknownPulse_min, type= 'ol')

ES01_unknownPulse_min <- read.csv(here("data/ES01_unknownPulse_minData.csv"))
ES01_unknownPulse_min$UTC <- as.POSIXct(ES01_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES01_unknownPulse_minOL <- createOctaveLevel(ES01_unknownPulse_min, type= 'ol')

CB01_unknownPulse_min <- read.csv(here("data/CB01_unknownPulse_minData.csv"))
CB01_unknownPulse_min$UTC <- as.POSIXct(CB01_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB01_unknownPulse_minOL <- createOctaveLevel(CB01_unknownPulse_min, type= 'ol')


DB01_unknownPulse_minOL <- DB01_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
DB01_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(DB01_unknownPulse_minOL)) { 
  if (DB01_unknownPulse_minOL$UTC_hour[c] == "") { 
    DB01_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}

DB01Unknown_minOLMed <- DB01_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
DB01Unknown_minOLQuants <- DB01_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
DB01Unknown_minOLMedQuants <- DB01Unknown_minOLMed %>%
  full_join(DB01Unknown_minOLQuants)
DB01Unknown_minOLMedQuants$site <- "DB01"
#DB01Unknown_minOLMedQuants$UTC_hour <- hms(DB01Unknown_minOLMedQuants$UTC_hour)
#DB01Unknown_minOLMedQuants$hour <- hour(DB01Unknown_minOLMedQuants$UTC_hour)



ES01_unknownPulse_minOL <- ES01_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
ES01_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(ES01_unknownPulse_minOL)) { 
  if (ES01_unknownPulse_minOL$UTC_hour[c] == "") { 
    ES01_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
ES01Unknown_minOLMed <- ES01_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
ES01Unknown_minOLQuants <- ES01_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
ES01Unknown_minOLMedQuants <- ES01Unknown_minOLMed %>%
  full_join(ES01Unknown_minOLQuants)
ES01Unknown_minOLMedQuants$site <- "ES01"
#ES01Unknown_minOLMedQuants$UTC_hour <- hms(ES01Unknown_minOLMedQuants$UTC_hour)
#ES01Unknown_minOLMedQuants$hour <- hour(ES01Unknown_minOLMedQuants$UTC_hour)


CB01_unknownPulse_minOL <- CB01_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
CB01_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(CB01_unknownPulse_minOL)) { 
  if (CB01_unknownPulse_minOL$UTC_hour[c] == "") { 
    CB01_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
CB01Unknown_minOLMed <- CB01_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
CB01Unknown_minOLQuants <- CB01_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
CB01Unknown_minOLMedQuants <- CB01Unknown_minOLMed %>%
  full_join(CB01Unknown_minOLQuants)
CB01Unknown_minOLMedQuants$site <- "CB01"
#CB01Unknown_minOLMedQuants$UTC_hour <- hms(CB01Unknown_minOLMedQuants$UTC_hour)
#CB01Unknown_minOLMedQuants$hour <- hour(CB01Unknown_minOLMedQuants$UTC_hour)


all_inUnknown_minOL <- DB01Unknown_minOLMedQuants %>%
  full_join(ES01Unknown_minOLMedQuants) %>%
  full_join(CB01Unknown_minOLMedQuants)

all_inUnknown_minOL$site = factor(all_inUnknown_minOL$site,
                                        levels= c("DB01", "ES01", "CB01"),
                                        labels= c("DB01", "ES01", "CB01"))
all_inUnknown_minOL$UTC_hour = as.POSIXct(strptime(all_inUnknown_minOL$UTC_hour,"%H:%M:%S", tz= "GMT"))

ggplot(all_inUnknown_minOL, aes(x= UTC_hour, y= med_500, group= site, color= site))+
  geom_ribbon(aes(ymin= quant10_500,
                  ymax= quant90_500,
                  fill= site, color= site), linetype= 0, linewidth= 0.2, alpha= 0.1)+
  scale_fill_manual(values= c("#00797F",  "#003087",  "#B71300"))+
  guides(fill= guide_legend(title= "Site"))+
  scale_x_datetime(breaks = breaks_width("1 hour"),labels=date_format("%H:%M"), minor_breaks = NULL)+
  geom_point(size= 1.5) + geom_line()+
  theme_bw()+
  xlab("Hour (UTC)")+
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  ggtitle("Unknown pulse full effort")+
  scale_color_manual(values= c("#00797F",  "#003087",  "#B71300"))+
  guides(color= guide_legend(title= "Site"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size= 16),
        axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        plot.title = element_text(size= 19),
        legend.title= element_text(size= 18),
        legend.text= element_text(size= 16))

#Mid-shore unknown pulse####
DB02_unknownPulse_min <- read.csv(here("data/DB02_unknownPulse_minData.csv"))
DB02_unknownPulse_min$UTC <- as.POSIXct(DB02_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB02_unknownPulse_minOL <- createOctaveLevel(DB02_unknownPulse_min, type= 'ol')

ES02_unknownPulse_min <- read.csv(here("data/ES02_unknownPulse_minData.csv"))
ES02_unknownPulse_min$UTC <- as.POSIXct(ES02_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES02_unknownPulse_minOL <- createOctaveLevel(ES02_unknownPulse_min, type= 'ol')

CB02_unknownPulse_min <- read.csv(here("data/CB02_unknownPulse_minData.csv"))
CB02_unknownPulse_min$UTC <- as.POSIXct(CB02_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB02_unknownPulse_minOL <- createOctaveLevel(CB02_unknownPulse_min, type= 'ol')

CB03_unknownPulse_min <- read.csv(here("data/CB03_unknownPulse_minData.csv"))
CB03_unknownPulse_min$UTC <- as.POSIXct(CB03_unknownPulse_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB03_unknownPulse_minOL <- createOctaveLevel(CB03_unknownPulse_min, type= 'ol')

#Unknown pulse
DB02_unknownPulse_minOL <- DB02_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
DB02_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(DB02_unknownPulse_minOL)) { 
  if (DB02_unknownPulse_minOL$UTC_hour[c] == "") { 
    DB02_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}

DB02Unknown_minOLMed <- DB02_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
DB02Unknown_minOLQuants <- DB02_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
DB02Unknown_minOLMedQuants <- DB02Unknown_minOLMed %>%
  full_join(DB02Unknown_minOLQuants)
DB02Unknown_minOLMedQuants$site <- "DB02"
#DB02Unknown_minOLMedQuants$UTC_hour <- hms(DB02Unknown_minOLMedQuants$UTC_hour)
#DB02Unknown_minOLMedQuants$hour <- hour(DB02Unknown_minOLMedQuants$UTC_hour)



ES02_unknownPulse_minOL <- ES02_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
ES02_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(ES02_unknownPulse_minOL)) { 
  if (ES02_unknownPulse_minOL$UTC_hour[c] == "") { 
    ES02_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
ES02Unknown_minOLMed <- ES02_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
ES02Unknown_minOLQuants <- ES02_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
ES02Unknown_minOLMedQuants <- ES02Unknown_minOLMed %>%
  full_join(ES02Unknown_minOLQuants)
ES02Unknown_minOLMedQuants$site <- "ES02"
#ES02Unknown_minOLMedQuants$UTC_hour <- hms(ES02Unknown_minOLMedQuants$UTC_hour)
#ES02Unknown_minOLMedQuants$hour <- hour(ES02Unknown_minOLMedQuants$UTC_hour)


CB02_unknownPulse_minOL <- CB02_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
CB02_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(CB02_unknownPulse_minOL)) { 
  if (CB02_unknownPulse_minOL$UTC_hour[c] == "") { 
    CB02_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
CB02Unknown_minOLMed <- CB02_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
CB02Unknown_minOLQuants <- CB02_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
CB02Unknown_minOLMedQuants <- CB02Unknown_minOLMed %>%
  full_join(CB02Unknown_minOLQuants)
CB02Unknown_minOLMedQuants$site <- "CB02"
#CB02Unknown_minOLMedQuants$UTC_hour <- hms(CB02Unknown_minOLMedQuants$UTC_hour)
#CB02Unknown_minOLMedQuants$hour <- hour(CB02Unknown_minOLMedQuants$UTC_hour)


CB03_unknownPulse_minOL <- CB03_unknownPulse_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
CB03_unknownPulse_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(CB03_unknownPulse_minOL)) { 
  if (CB03_unknownPulse_minOL$UTC_hour[c] == "") { 
    CB03_unknownPulse_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
CB03Unknown_minOLMed <- CB03_unknownPulse_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
quants= c(0.1, 0.9)
CB03Unknown_minOLQuants <- CB03_unknownPulse_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_500 = quantile(OL_500, probs= quants[1], na.rm= TRUE),
            quant90_500 = quantile(OL_500, probs= quants[2], na.rm= TRUE))
CB03Unknown_minOLMedQuants <- CB03Unknown_minOLMed %>%
  full_join(CB03Unknown_minOLQuants)
CB03Unknown_minOLMedQuants$site <- "CB03"

all_midUnknown_minOL <- DB02Unknown_minOLMedQuants %>%
  full_join(ES02Unknown_minOLMedQuants) %>%
  full_join(CB02Unknown_minOLMedQuants) %>%
  full_join(CB03Unknown_minOLMedQuants)

all_midUnknown_minOL$site = factor(all_midUnknown_minOL$site,
                                        levels= c("DB02", "ES02", "CB02", "CB03"),
                                        labels= c("DB02", "ES02", "CB02", "CB03"))
all_midUnknown_minOL$UTC_hour = as.POSIXct(strptime(all_midUnknown_minOL$UTC_hour,"%H:%M:%S", tz= "GMT"))

ggplot(all_midUnknown_minOL, aes(x= UTC_hour, y= med_500, group= site, color= site))+
  geom_ribbon(aes(ymin= quant10_500,
                  ymax= quant90_500,
                  fill= site, color= site), linetype= 0, linewidth= 0.2, alpha= 0.1)+
  scale_fill_manual(values= c("#00797F",  "#003087",  "#B71300", "purple"))+
  guides(fill= guide_legend(title= "Site"))+
  scale_x_datetime(breaks = breaks_width("1 hour"),labels=date_format("%H:%M"), minor_breaks = NULL)+
  geom_point(size= 1.5) + geom_line()+
  theme_bw()+
  xlab("Hour (UTC)")+
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  ggtitle("Unknown pulse full effort")+
  scale_color_manual(values= c("#00797F",  "#003087",  "#B71300", "purple"))+
  guides(color= guide_legend(title= "Site"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size= 16),
        axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        plot.title = element_text(size= 19),
        legend.title= element_text(size= 18),
        legend.text= element_text(size= 16))

#Inshore cusk eel####
DB01_cuskEel_min <- read.csv(here("data/DB01_cuskEel_minData.csv"))
DB01_cuskEel_min$UTC <- as.POSIXct(DB01_cuskEel_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
DB01_cuskEel_minOL <- createOctaveLevel(DB01_cuskEel_min, type= 'ol')

ES01_cuskEel_min <- read.csv(here("data/ES01_cuskEel_minData.csv"))
ES01_cuskEel_min$UTC <- as.POSIXct(ES01_cuskEel_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
ES01_cuskEel_minOL <- createOctaveLevel(ES01_cuskEel_min, type= 'ol')

CB01_cuskEel_min <- read.csv(here("data/CB01_cuskEel_minData.csv"))
CB01_cuskEel_min$UTC <- as.POSIXct(CB01_cuskEel_min$UTC, format= "%Y-%m-%dT%H:%M:%SZ", tz = "GMT")
CB01_cuskEel_minOL <- createOctaveLevel(CB01_cuskEel_min, type= 'ol')

DB01_cuskEel_minOL <- DB01_cuskEel_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
DB01_cuskEel_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(DB01_cuskEel_minOL)) { 
  if (DB01_cuskEel_minOL$UTC_hour[c] == "") { 
    DB01_cuskEel_minOL$UTC_hour[c] <- "00:00:00" 
  }
}

DB01cuskEel_minOLMed <- DB01_cuskEel_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
quants= c(0.1, 0.9)
DB01cuskEel_minOLQuants <- DB01_cuskEel_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_2000 = quantile(OL_2000, probs= quants[1], na.rm= TRUE),
            quant90_2000 = quantile(OL_2000, probs= quants[2], na.rm= TRUE))
DB01cuskEel_minOLMedQuants <- DB01cuskEel_minOLMed %>%
  full_join(DB01cuskEel_minOLQuants)
DB01cuskEel_minOLMedQuants$site <- "DB01"
#DB01cuskEel_minOLMedQuants$UTC_hour <- hms(DB01cuskEel_minOLMedQuants$UTC_hour)
#DB01cuskEel_minOLMedQuants$hour <- hour(DB01cuskEel_minOLMedQuants$UTC_hour)



ES01_cuskEel_minOL <- ES01_cuskEel_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
ES01_cuskEel_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(ES01_cuskEel_minOL)) { 
  if (ES01_cuskEel_minOL$UTC_hour[c] == "") { 
    ES01_cuskEel_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
ES01cuskEel_minOLMed <- ES01_cuskEel_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
quants= c(0.1, 0.9)
ES01cuskEel_minOLQuants <- ES01_cuskEel_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_2000 = quantile(OL_2000, probs= quants[1], na.rm= TRUE),
            quant90_2000 = quantile(OL_2000, probs= quants[2], na.rm= TRUE))
ES01cuskEel_minOLMedQuants <- ES01cuskEel_minOLMed %>%
  full_join(ES01cuskEel_minOLQuants)
ES01cuskEel_minOLMedQuants$site <- "ES01"
#ES01cuskEel_minOLMedQuants$UTC_hour <- hms(ES01cuskEel_minOLMedQuants$UTC_hour)
#ES01cuskEel_minOLMedQuants$hour <- hour(ES01cuskEel_minOLMedQuants$UTC_hour)


CB01_cuskEel_minOL <- CB01_cuskEel_minOL %>%
  mutate(UTC_date = str_split(UTC," ", simplify = T)[,1]) %>%
  mutate(UTC_hour =  str_split(UTC," ", simplify = T)[,2])
CB01_cuskEel_minOL %>% filter(UTC_hour == "") %>% nrow 
for (c in 1:nrow(CB01_cuskEel_minOL)) { 
  if (CB01_cuskEel_minOL$UTC_hour[c] == "") { 
    CB01_cuskEel_minOL$UTC_hour[c] <- "00:00:00" 
  }
}
CB01cuskEel_minOLMed <- CB01_cuskEel_minOL%>%
  dplyr::group_by(UTC_hour)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
quants= c(0.1, 0.90)
CB01cuskEel_minOLQuants <- CB01_cuskEel_minOL %>%
   group_by(UTC_hour) %>%
  summarize(quant10_2000 = quantile(OL_2000, probs= quants[1], na.rm= TRUE),
            quant90_2000 = quantile(OL_2000, probs= quants[2], na.rm= TRUE))
CB01cuskEel_minOLMedQuants <- CB01cuskEel_minOLMed %>%
  full_join(CB01cuskEel_minOLQuants)
CB01cuskEel_minOLMedQuants$site <- "CB01"
#CB01cuskEel_minOLMedQuants$UTC_hour <- hms(CB01cuskEel_minOLMedQuants$UTC_hour)
#CB01cuskEel_minOLMedQuants$hour <- hour(CB01cuskEel_minOLMedQuants$UTC_hour)


all_incuskEel_minOL <- DB01cuskEel_minOLMedQuants %>%
  full_join(ES01cuskEel_minOLMedQuants) %>%
  full_join(CB01cuskEel_minOLMedQuants)

all_incuskEel_minOL$site = factor(all_incuskEel_minOL$site,
                                        levels= c("DB01", "ES01", "CB01"),
                                        labels= c("DB01", "ES01", "CB01"))
all_incuskEel_minOL$UTC_hour = as.POSIXct(strptime(all_incuskEel_minOL$UTC_hour,"%H:%M:%S", tz= "GMT"))

ggplot(all_incuskEel_minOL, aes(x= UTC_hour, y= med_2000, group= site, color= site))+
  geom_ribbon(aes(ymin= quant10_2000,
                  ymax= quant90_2000,
                  fill= site, color= site), linetype= 0, linewidth= 0.2, alpha= 0.1)+
  scale_fill_manual(values= c("#00797F",  "#003087",  "#B71300"))+
  guides(fill= guide_legend(title= "Site"))+
  scale_x_datetime(breaks = breaks_width("1 hour"),labels=date_format("%H:%M"), minor_breaks = NULL)+
  geom_point(size= 1.5) + geom_line()+
  theme_bw()+
  xlab("Hour (UTC)")+
  ylab(expression(paste('Median 2000Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  ggtitle("Cusk Eel full effort")+
  scale_color_manual(values= c("#00797F",  "#003087",  "#B71300"))+
  guides(color= guide_legend(title= "Site"))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size= 16),
        axis.title= element_text(size= 18),
        axis.text.y= element_text(size= 16),
        plot.title = element_text(size= 19),
        legend.title= element_text(size= 18),
        legend.text= element_text(size= 16))



```
#Chorus onset: unknown pulse
```{r}
  #DB01- onset days: 8/16/2022 (00:00), 5/25/2023 (01:00), 5/21/2024 (01:00) --> naut dusk
  #ES01- onset days: 10/15/2023 (23:00), 7/23/2024 (01:00)
  #CB01- onset days: 6/13/2022 (01:00), 5/12/2023 (01:00), 5/23/2024 (01:00)
  #DB02- onset days: 10/3/2022 (22:00), 9/24/2023 (22:00), 9/18/2024 (23:00)--> sunset
  #ES02- onset days: 10/15/2023 (22:00), 9/20/2024 (22:00)
  #CB02- onset days: 9/10/2022 (23:00), 9/16/2023 (23:00), 9/18/2024 (23:00)
  #CB03- onset days: 8/8/2022 (0) OR 9/10/2022 (23), 9/15/2023 (23), 9/16/2024 (23)

  #DB01 onset days####
#DB01_81622 <-  format(seq(ymd_hms("2022-08-16 00:00:00"), ymd_hms("2022-08-16 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#DB01_81622df <- data.frame(UTC= DB01_81622)
#DB01_81622df$UTC <- as.POSIXct(DB01_81622df$UTC)
#DB01_81622df <-DB01_81622df %>%
#  left_join(DB01_unknownPulse_minOL, by= "UTC")
#DB01_81622df$hour <- hour(DB01_81622df$UTC)
#DB01_81622df <- DB01_81622df %>%
#  filter(DB01_81622df$hour== c("0"))
#DB01_81622Med <- DB01_81622df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#DB01_81622Med$site <- "DB01"
#DB01_81622Med$season <- "Summer"

DB01_52523 <-  format(seq(ymd_hms("2023-05-25 00:00:00"), ymd_hms("2023-05-25 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
DB01_52523df <- data.frame(UTC= DB01_52523)
DB01_52523df$UTC <- as.POSIXct(DB01_52523df$UTC)
DB01_52523df <-DB01_52523df %>%
  left_join(DB01_unknownPulse_minOL, by= "UTC")
DB01_52523df$hour <- hour(DB01_52523df$UTC)
DB01_52523df <- DB01_52523df %>%
  filter(DB01_52523df$hour== c("1"))
DB01_52523Med <- DB01_52523df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB01_52523Med$site <- "DB01"
DB01_52523Med$season <- "Spring"

DB01_52124 <-  format(seq(ymd_hms("2024-05-21 00:00:00"), ymd_hms("2024-05-21 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
DB01_52124df <- data.frame(UTC= DB01_52124)
DB01_52124df$UTC <- as.POSIXct(DB01_52124df$UTC)
DB01_52124df <-DB01_52124df %>%
  left_join(DB01_unknownPulse_minOL, by= "UTC")
DB01_52124df$hour <- hour(DB01_52124df$UTC)
DB01_52124df <- DB01_52124df %>%
  filter(DB01_52124df$hour== c("1"))
DB01_52124Med <- DB01_52124df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB01_52124Med$site <- "DB01"
DB01_52124Med$season <- "Spring"

DB01_unknownPulse_onsets <- DB01_52523Med %>%
  full_join(DB01_52124Med)

DB01_unknownPulse_onsets <- DB01_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB01_unknownPulse_onsets$month_day <- paste(DB01_unknownPulse_onsets$month, DB01_unknownPulse_onsets$day, sep = "-")
DB01_unknownPulse_onsets$shore <- "Inshore"
DB01_unknownPulse_onsets$lat <- "Delaware"


  #ES01 onset days####
#ES01_101523 <-  format(seq(ymd_hms("2023-10-14 20:00:00"), ymd_hms("2023-10-15 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#ES01_101523df <- data.frame(UTC= ES01_101523)
#ES01_101523df$UTC <- as.POSIXct(ES01_101523df$UTC)
#ES01_101523df <-ES01_101523df %>%
#  left_join(ES01_unknownPulse_minOL, by= "UTC")
#ES01_101523df$hour <- hour(ES01_101523df$UTC)
#ES01_101523df <- ES01_101523df %>%
#  filter(ES01_101523df$hour== c("23"))
#ES01_101523Med <- ES01_101523df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#ES01_101523Med$site <- "ES01"
#ES01_101523Med$season <- "Fall"

ES01_72324 <-  format(seq(ymd_hms("2024-07-23 00:00:00"), ymd_hms("2024-07-23 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
ES01_72324df <- data.frame(UTC= ES01_72324)
ES01_72324df$UTC <- as.POSIXct(ES01_72324df$UTC)
ES01_72324df <-ES01_72324df %>%
  left_join(ES01_unknownPulse_minOL, by= "UTC")
ES01_72324df$hour <- hour(ES01_72324df$UTC)
ES01_72324df <- ES01_72324df %>%
  filter(ES01_72324df$hour== c("1"))
ES01_72324Med <- ES01_72324df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
ES01_72324Med$site <- "ES01"
ES01_72324Med$season <- "Summer"

ES01_unknownPulse_onsets <- ES01_72324Med

ES01_unknownPulse_onsets <- ES01_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES01_unknownPulse_onsets$month_day <- paste(ES01_unknownPulse_onsets$month, ES01_unknownPulse_onsets$day, sep = "-")
ES01_unknownPulse_onsets$shore <- "Inshore"
ES01_unknownPulse_onsets$lat <- "Eastern"


  #CB01 onset days####
#CB01_61322 <-  format(seq(ymd_hms("2022-06-12 20:00:00"), ymd_hms("2022-06-13 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB01_61322df <- data.frame(UTC= CB01_61322)
#CB01_61322df$UTC <- as.POSIXct(CB01_61322df$UTC)
#CB01_61322df <-CB01_61322df %>%
#  left_join(CB01_unknownPulse_minOL, by= "UTC")
#CB01_61322df$hour <- hour(CB01_61322df$UTC)
#CB01_61322df <- CB01_61322df %>%
#  filter(CB01_61322df$hour== c("1"))
#CB01_61322Med <- CB01_61322df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB01_61322Med$site <- "CB01"
#CB01_61322Med$season <- "Summer"

CB01_51223 <-  format(seq(ymd_hms("2023-05-12 00:00:00"), ymd_hms("2023-05-12 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
CB01_51223df <- data.frame(UTC= CB01_51223)
CB01_51223df$UTC <- as.POSIXct(CB01_51223df$UTC)
CB01_51223df <-CB01_51223df %>%
  left_join(CB01_unknownPulse_minOL, by= "UTC")
CB01_51223df$hour <- hour(CB01_51223df$UTC)
CB01_51223df <- CB01_51223df %>%
  filter(CB01_51223df$hour== c("1"))
CB01_51223Med <- CB01_51223df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB01_51223Med$site <- "CB01"
CB01_51223Med$season <- "Spring"

#CB01_52324 <-  format(seq(ymd_hms("2024-05-23 00:00:00"), ymd_hms("2024-05-23 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB01_52324df <- data.frame(UTC= CB01_52324)
#CB01_52324df$UTC <- as.POSIXct(CB01_52324df$UTC)
#CB01_52324df <-CB01_52324df %>%
 # left_join(CB01_unknownPulse_minOL, by= "UTC")
#CB01_52324df$hour <- hour(CB01_52324df$UTC)
#CB01_52324df <- CB01_52324df %>%
#  filter(CB01_52324df$hour== c("1"))
#CB01_52324Med <- CB01_52324df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
 #   med_500= median(OL_500, na.rm= TRUE))
#CB01_52324Med$site <- "CB01"
#CB01_52324Med$season <- "Spring"

CB01_unknownPulse_onsets <- CB01_51223Med 

CB01_unknownPulse_onsets <- CB01_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB01_unknownPulse_onsets$month_day <- paste(CB01_unknownPulse_onsets$month, CB01_unknownPulse_onsets$day, sep = "-")
CB01_unknownPulse_onsets$shore <- "Inshore"
CB01_unknownPulse_onsets$lat <- "Chesapeake"

  #DB02 onset days####
#DB02_10322 <-  format(seq(ymd_hms("2022-10-02 20:00:00"), ymd_hms("2022-10-03 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#DB02_10322df <- data.frame(UTC= DB02_10322)
#DB02_10322df$UTC <- as.POSIXct(DB02_10322df$UTC)
#DB02_10322df <-DB02_10322df %>%
#  left_join(DB02_unknownPulse_minOL, by= "UTC")
#DB02_10322df$hour <- hour(DB02_10322df$UTC)
#DB02_10322df <- DB02_10322df %>%
#  filter(DB02_10322df$hour== c("22"))
#DB02_10322Med <- DB02_10322df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#DB02_10322Med$site <- "DB02"
#DB02_10322Med$season <- "Fall"

DB02_92423 <-  format(seq(ymd_hms("2023-09-24 00:00:00"), ymd_hms("2023-09-24 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
DB02_92423df <- data.frame(UTC= DB02_92423)
DB02_92423df$UTC <- as.POSIXct(DB02_92423df$UTC)
DB02_92423df <-DB02_92423df %>%
  left_join(DB02_unknownPulse_minOL, by= "UTC")
DB02_92423df$hour <- hour(DB02_92423df$UTC)
DB02_92423df <- DB02_92423df %>%
  filter(DB02_92423df$hour== c("22"))
DB02_92423Med <- DB02_92423df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB02_92423Med$site <- "DB02"
DB02_92423Med$season <- "Fall"

DB02_91824 <-  format(seq(ymd_hms("2024-09-18 00:00:00"), ymd_hms("2024-09-18 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
DB02_91824df <- data.frame(UTC= DB02_91824)
DB02_91824df$UTC <- as.POSIXct(DB02_91824df$UTC)
DB02_91824df <-DB02_91824df %>%
  left_join(DB02_unknownPulse_minOL, by= "UTC")
DB02_91824df$hour <- hour(DB02_91824df$UTC)
DB02_91824df <- DB02_91824df %>%
  filter(DB02_91824df$hour== c("23"))
DB02_91824Med <- DB02_91824df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB02_91824Med$site <- "DB02"
DB02_91824Med$season <- "Fall"

DB02_unknownPulse_onsets <-DB02_92423Med %>%
  full_join(DB02_91824Med)

DB02_unknownPulse_onsets <- DB02_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB02_unknownPulse_onsets$month_day <- paste(DB02_unknownPulse_onsets$month, DB02_unknownPulse_onsets$day, sep = "-")
DB02_unknownPulse_onsets$shore <- "Mid-shore"
DB02_unknownPulse_onsets$lat <- "Delaware"


  #ES02 onset days####
#ES02_101523 <-  format(seq(ymd_hms("2023-10-14 20:00:00"), ymd_hms("2023-10-15 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#ES02_101523df <- data.frame(UTC= ES02_101523)
#ES02_101523df$UTC <- as.POSIXct(ES02_101523df$UTC)
#ES02_101523df <-ES02_101523df %>%
#  left_join(ES02_unknownPulse_minOL, by= "UTC")
#ES02_101523df$hour <- hour(ES02_101523df$UTC)
#ES02_101523df <- ES02_101523df %>%
#  filter(ES02_101523df$hour== c("22"))
#ES02_101523Med <- ES02_101523df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#ES02_101523Med$site <- "ES02"
#ES02_101523Med$season <- "Fall"

ES02_92024 <-  format(seq(ymd_hms("2024-09-20 00:00:00"), ymd_hms("2024-09-20 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
ES02_92024df <- data.frame(UTC= ES02_92024)
ES02_92024df$UTC <- as.POSIXct(ES02_92024df$UTC)
ES02_92024df <-ES02_92024df %>%
  left_join(ES02_unknownPulse_minOL, by= "UTC")
ES02_92024df$hour <- hour(ES02_92024df$UTC)
ES02_92024df <- ES02_92024df %>%
  filter(ES02_92024df$hour== c("22"))
ES02_92024Med <- ES02_92024df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
ES02_92024Med$site <- "ES02"
ES02_92024Med$season <- "Fall"

ES02_unknownPulse_onsets <- ES02_92024Med

ES02_unknownPulse_onsets <- ES02_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES02_unknownPulse_onsets$month_day <- paste(ES02_unknownPulse_onsets$month, ES02_unknownPulse_onsets$day, sep = "-")
ES02_unknownPulse_onsets$shore <- "Mid-shore"
ES02_unknownPulse_onsets$lat <- "Eastern"

  #CB02 onset days####
#CB02_91022 <-  format(seq(ymd_hms("2022-09-09 20:00:00"), ymd_hms("2022-09-10 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB02_91022df <- data.frame(UTC= CB02_91022)
#CB02_91022df$UTC <- as.POSIXct(CB02_91022df$UTC)
#CB02_91022df <-CB02_91022df %>%
#  left_join(CB02_unknownPulse_minOL, by= "UTC")
#CB02_91022df$hour <- hour(CB02_91022df$UTC)
#CB02_91022df <- CB02_91022df %>%
 # filter(CB02_91022df$hour== c("23"))
#CB02_91022Med <- CB02_91022df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB02_91022Med$site <- "CB02"
#CB02_91022Med$season <- "Fall"

CB02_91623 <-  format(seq(ymd_hms("2023-09-16 00:00:00"), ymd_hms("2023-09-16 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
CB02_91623df <- data.frame(UTC= CB02_91623)
CB02_91623df$UTC <- as.POSIXct(CB02_91623df$UTC)
CB02_91623df <-CB02_91623df %>%
  left_join(CB02_unknownPulse_minOL, by= "UTC")
CB02_91623df$hour <- hour(CB02_91623df$UTC)
CB02_91623df <- CB02_91623df %>%
  filter(CB02_91623df$hour== c("23"))
CB02_91623Med <- CB02_91623df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB02_91623Med$site <- "CB02"
CB02_91623Med$season <- "Fall"

CB02_91824 <-  format(seq(ymd_hms("2024-09-18 00:00:00"), ymd_hms("2024-09-18 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
CB02_91824df <- data.frame(UTC= CB02_91824)
CB02_91824df$UTC <- as.POSIXct(CB02_91824df$UTC)
CB02_91824df <-CB02_91824df %>%
  left_join(CB02_unknownPulse_minOL, by= "UTC")
CB02_91824df$hour <- hour(CB02_91824df$UTC)
CB02_91824df <- CB02_91824df %>%
  filter(CB02_91824df$hour== c("23"))
CB02_91824Med <- CB02_91824df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB02_91824Med$site <- "CB02"
CB02_91824Med$season <- "Fall"

CB02_unknownPulse_onsets <- CB02_91623Med %>%
  full_join(CB02_91824Med)

CB02_unknownPulse_onsets <- CB02_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB02_unknownPulse_onsets$month_day <- paste(CB02_unknownPulse_onsets$month, CB02_unknownPulse_onsets$day, sep = "-")
CB02_unknownPulse_onsets$shore <- "Mid-shore"
CB02_unknownPulse_onsets$lat <- "Chesapeake"


  #CB03 onset days####
#CB03_8822 <-  format(seq(ymd_hms("2022-08-07 20:00:00"), ymd_hms("2022-08-08 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB03_8822df <- data.frame(UTC= CB03_8822)
#CB03_8822df$UTC <- as.POSIXct(CB03_8822df$UTC)
#CB03_8822df <-CB03_8822df %>%
#  left_join(CB03_unknownPulse_minOL, by= "UTC")
#CB03_8822df$hour <- hour(CB03_8822df$UTC)
#CB03_8822df <- CB03_8822df %>%
#  filter(CB03_8822df$hour== c("0"))
#CB03_8822Med <- CB03_8822df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB03_8822Med$site <- "CB03"
#CB03_8822Med$season <- "Summer"

CB03_91523 <-  format(seq(ymd_hms("2023-09-15 00:00:00"), ymd_hms("2023-09-15 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
CB03_91523df <- data.frame(UTC= CB03_91523)
CB03_91523df$UTC <- as.POSIXct(CB03_91523df$UTC)
CB03_91523df <-CB03_91523df %>%
  left_join(CB03_unknownPulse_minOL, by= "UTC")
CB03_91523df$hour <- hour(CB03_91523df$UTC)
CB03_91523df <- CB03_91523df %>%
  filter(CB03_91523df$hour== c("23"))
CB03_91523Med <- CB03_91523df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB03_91523Med$site <- "CB03"
CB03_91523Med$season <- "Fall"

CB03_91624 <-  format(seq(ymd_hms("2024-09-16 00:00:00"), ymd_hms("2024-09-16 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
CB03_91624df <- data.frame(UTC= CB03_91624)
CB03_91624df$UTC <- as.POSIXct(CB03_91624df$UTC)
CB03_91624df <-CB03_91624df %>%
  left_join(CB03_unknownPulse_minOL, by= "UTC")
CB03_91624df$hour <- hour(CB03_91624df$UTC)
CB03_91624df <- CB03_91624df %>%
  filter(CB03_91624df$hour== c("23"))
CB03_91624Med <- CB03_91624df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB03_91624Med$site <- "CB03"
CB03_91624Med$season <- "Fall"

CB03_unknownPulse_onsets <- CB03_91523Med %>%
  full_join(CB03_91624Med)

CB03_unknownPulse_onsets <- CB03_unknownPulse_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB03_unknownPulse_onsets$month_day <- paste(CB03_unknownPulse_onsets$month, CB03_unknownPulse_onsets$day, sep = "-")
CB03_unknownPulse_onsets$shore <- "Mid-shore"
CB03_unknownPulse_onsets$lat <- "Chesapeake"




#combining####
inshore_unknownPulse_onsets <- DB01_unknownPulse_onsets %>%
#  full_join(ES01_unknownPulse_onsets) %>%
  full_join(CB01_unknownPulse_onsets)
midshore_unknownPulse_onsets <- DB02_unknownPulse_onsets %>%
#  full_join(ES02_unknownPulse_onsets) %>%
  full_join(CB02_unknownPulse_onsets) %>%
  full_join(CB03_unknownPulse_onsets)
all_unknownPulse_onsets <- inshore_unknownPulse_onsets %>%
  full_join(midshore_unknownPulse_onsets)

```
#Chorus peak: unknown pulse
```{r}
#Unknown pulse####
  #DB01- peak days: 9/20/2022 (at 23:45), 6/12/2023 (01:45), 9/12/2024 (00:15)
  #ES01- peak days: 10/15/2023 (00:00), 9/12/2024 (00:30)
  #CB01- peak days: 8/20/2022 (00:45), 8/16/2023 (01:45), 09/04/2024 (00:30)
  #DB02- peak days: 10/3/2022 (22:30), 10/1/2023 (23:30), 9/26/2024 (23:45)
  #ES02- peak days: 10/15/2023 (23:15), 9/27/2024 (23:30)
  #CB02- peak days: 10/5/2022 (00:00), 9/27/2023 (23:30), 9/24/2024 (23:45)

CB03_unknownPulse_minOL$year <- year(CB03_unknownPulse_minOL$UTC)
CB03_unknownPulse_peaks <- CB03_unknownPulse_minOL %>%
  group_by(year) %>%
  slice_max(OL_500)

  #DB01 peak days####
#DB01_92022 <-  format(seq(ymd_hms("2022-09-19 20:00:00"), ymd_hms("2022-09-20 19:45:00"), by = "15 min")) 
#DB01_92022df <- data.frame(UTC= DB01_92022)
#DB01_92022df$UTC <- as.POSIXct(DB01_92022df$UTC)
#DB01_92022df <-DB01_92022df %>%
#  left_join(DB01_unknownPulse_minOL, by= "UTC")
#DB01_92022df$hour <- hour(DB01_92022df$UTC)
#DB01_92022df <- DB01_92022df %>%
#  filter(DB01_92022df$hour== c("23"))
#DB01_92022Med <- DB01_92022df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#DB01_92022Med$site <- "DB01"

DB01_61223 <-  format(seq(ymd_hms("2023-06-12 00:00:00"), ymd_hms("2023-06-12 23:45:00"), by = "15 min")) 
DB01_61223df <- data.frame(UTC= DB01_61223)
DB01_61223df$UTC <- as.POSIXct(DB01_61223df$UTC)
DB01_61223df <-DB01_61223df %>%
  left_join(DB01_unknownPulse_minOL, by= "UTC")
DB01_61223df$hour <- hour(DB01_61223df$UTC)
DB01_61223df <- DB01_61223df %>%
  filter(DB01_61223df$hour== c("1"))
DB01_61223Med <- DB01_61223df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB01_61223Med$site <- "DB01"

DB01_91224 <-  format(seq(ymd_hms("2024-09-12 00:00:00"), ymd_hms("2024-09-12 23:45:00"), by = "15 min")) 
DB01_91224df <- data.frame(UTC= DB01_91224)
DB01_91224df$UTC <- as.POSIXct(DB01_91224df$UTC)
DB01_91224df <-DB01_91224df %>%
  left_join(DB01_unknownPulse_minOL, by= "UTC")
DB01_91224df$hour <- hour(DB01_91224df$UTC)
DB01_91224df <- DB01_91224df %>%
  filter(DB01_91224df$hour== c("0"))
DB01_91224Med <- DB01_91224df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB01_91224Med$site <- "DB01"

DB01_unknownPulse_peaks <- DB01_61223Med %>%
  full_join(DB01_91224Med)

DB01_unknownPulse_peaks <- DB01_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB01_unknownPulse_peaks$month_day <- paste(DB01_unknownPulse_peaks$month, DB01_unknownPulse_peaks$day, sep = "-")
DB01_unknownPulse_peaks$shore <- "Inshore"
DB01_unknownPulse_peaks$lat <- "Delaware"

  #ES01 peak days####
#ES01_101523 <-  format(seq(ymd_hms("2023-10-14 20:00:00"), ymd_hms("2023-10-15 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#ES01_101523df <- data.frame(UTC= ES01_101523)
#ES01_101523df$UTC <- as.POSIXct(ES01_101523df$UTC)
#ES01_101523df <-ES01_101523df %>%
#  left_join(ES01_unknownPulse_minOL, by= "UTC")
#ES01_101523df$hour <- hour(ES01_101523df$UTC)
#ES01_101523df <- ES01_101523df %>%
#  filter(ES01_101523df$hour== c("0"))
#ES01_101523Med <- ES01_101523df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#ES01_101523Med$site <- "ES01"

ES01_91224 <-  format(seq(ymd_hms("2024-09-12 00:00:00"), ymd_hms("2024-09-12 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
ES01_91224df <- data.frame(UTC= ES01_91224)
ES01_91224df$UTC <- as.POSIXct(ES01_91224df$UTC)
ES01_91224df <-ES01_91224df %>%
  left_join(ES01_unknownPulse_minOL, by= "UTC")
ES01_91224df$hour <- hour(ES01_91224df$UTC)
ES01_91224df <- ES01_91224df %>%
  filter(ES01_91224df$hour== c("0"))
ES01_91224Med <- ES01_91224df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
ES01_91224Med$site <- "ES01"

ES01_unknownPulse_peaks <- ES01_91224Med

ES01_unknownPulse_peaks <- ES01_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES01_unknownPulse_peaks$month_day <- paste(ES01_unknownPulse_peaks$month, ES01_unknownPulse_peaks$day, sep = "-")
ES01_unknownPulse_peaks$shore <- "Inshore"
ES01_unknownPulse_peaks$lat <- "Eastern"

  #CB01 peak days####
#CB01_82022 <-  format(seq(ymd_hms("2022-08-19 20:00:00"), ymd_hms("2022-08-20 19:45:00"), by = "15 min")) 
#CB01_82022df <- data.frame(UTC= CB01_82022)
#CB01_82022df$UTC <- as.POSIXct(CB01_82022df$UTC)
#CB01_82022df <-CB01_82022df %>%
#  left_join(CB01_unknownPulse_minOL, by= "UTC")
#CB01_82022df$hour <- hour(CB01_82022df$UTC)
#CB01_82022df <- CB01_82022df %>%
#  filter(CB01_82022df$hour== c("0"))
#CB01_82022Med <- CB01_82022df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB01_82022Med$site <- "CB01"

CB01_81623 <-  format(seq(ymd_hms("2023-08-16 00:00:00"), ymd_hms("2023-08-16 23:45:00"), by = "15 min")) 
CB01_81623df <- data.frame(UTC= CB01_81623)
CB01_81623df$UTC <- as.POSIXct(CB01_81623df$UTC)
CB01_81623df <-CB01_81623df %>%
  left_join(CB01_unknownPulse_minOL, by= "UTC")
CB01_81623df$hour <- hour(CB01_81623df$UTC)
CB01_81623df <- CB01_81623df %>%
  filter(CB01_81623df$hour== c("1"))
CB01_81623Med <- CB01_81623df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB01_81623Med$site <- "CB01"

CB01_9424<-  format(seq(ymd_hms("2024-09-24 00:00:00"), ymd_hms("2024-09-24 23:45:00"), by = "15 min")) 
CB01_9424df <- data.frame(UTC= CB01_9424)
CB01_9424df$UTC <- as.POSIXct(CB01_9424df$UTC)
CB01_9424df <-CB01_9424df %>%
  left_join(CB01_unknownPulse_minOL, by= "UTC")
CB01_9424df$hour <- hour(CB01_9424df$UTC)
CB01_9424df <- CB01_9424df %>%
  filter(CB01_9424df$hour== c("0"))
CB01_9424Med <- CB01_9424df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB01_9424Med$site <- "CB01"

CB01_unknownPulse_peaks <- CB01_81623Med %>%
  full_join(CB01_9424Med)

CB01_unknownPulse_peaks <- CB01_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB01_unknownPulse_peaks$month_day <- paste(CB01_unknownPulse_peaks$month, CB01_unknownPulse_peaks$day, sep = "-")
CB01_unknownPulse_peaks$shore <- "Inshore"
CB01_unknownPulse_peaks$lat <- "Chesapeake"

  #DB02 peak days####
#DB02_10322 <-  format(seq(ymd_hms("2022-10-02 20:00:00"), ymd_hms("2022-10-03 19:45:00"), by = "15 min")) 
#DB02_10322df <- data.frame(UTC= DB02_10322)
#DB02_10322df$UTC <- as.POSIXct(DB02_10322df$UTC)
#DB02_10322df <-DB02_10322df %>%
#  left_join(DB02_unknownPulse_minOL, by= "UTC")
#DB02_10322df$hour <- hour(DB02_10322df$UTC)
#DB02_10322df <- DB02_10322df %>%
#  filter(DB02_10322df$hour== c("22"))
#DB02_10322Med <- DB02_10322df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#DB02_10322Med$site <- "DB02"

DB02_10123 <-  format(seq(ymd_hms("2023-10-01 00:00:00"), ymd_hms("2023-10-01 23:45:00"), by = "15 min")) 
DB02_10123df <- data.frame(UTC= DB02_10123)
DB02_10123df$UTC <- as.POSIXct(DB02_10123df$UTC)
DB02_10123df <-DB02_10123df %>%
  left_join(DB02_unknownPulse_minOL, by= "UTC")
DB02_10123df$hour <- hour(DB02_10123df$UTC)
DB02_10123df <- DB02_10123df %>%
  filter(DB02_10123df$hour== c("23"))
DB02_10123Med <- DB02_10123df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB02_10123Med$site <- "DB02"

DB02_92624 <-  format(seq(ymd_hms("2024-09-26 00:00:00"), ymd_hms("2024-09-26 23:45:00"), by = "15 min")) 
DB02_92624df <- data.frame(UTC= DB02_92624)
DB02_92624df$UTC <- as.POSIXct(DB02_92624df$UTC)
DB02_92624df <-DB02_92624df %>%
  left_join(DB02_unknownPulse_minOL, by= "UTC")
DB02_92624df$hour <- hour(DB02_92624df$UTC)
DB02_92624df <- DB02_92624df %>%
  filter(DB02_92624df$hour== c("23"))
DB02_92624Med <- DB02_92624df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
DB02_92624Med$site <- "DB02"

DB02_unknownPulse_peaks <- DB02_10123Med %>%
  full_join(DB02_92624Med)

DB02_unknownPulse_peaks <- DB02_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB02_unknownPulse_peaks$month_day <- paste(DB02_unknownPulse_peaks$month, DB02_unknownPulse_peaks$day, sep = "-")
DB02_unknownPulse_peaks$shore <- "Mid-shore"
DB02_unknownPulse_peaks$lat <- "Delaware"


  #ES02 peak days####
#ES02_101523 <-  format(seq(ymd_hms("2023-10-14 20:00:00"), ymd_hms("2023-10-15 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#ES02_101523df <- data.frame(UTC= ES02_101523)
#ES02_101523df$UTC <- as.POSIXct(ES02_101523df$UTC)
#ES02_101523df <-ES02_101523df %>%
 # left_join(ES02_unknownPulse_minOL, by= "UTC")
#ES02_101523df$hour <- hour(ES02_101523df$UTC)
#ES02_101523df <- ES02_101523df %>%
#  filter(ES02_101523df$hour== c("23"))
#ES02_101523Med <- ES02_101523df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#ES02_101523Med$site <- "ES02"

ES02_92724 <-  format(seq(ymd_hms("2024-09-27 00:00:00"), ymd_hms("2024-09-27 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
ES02_92724df <- data.frame(UTC= ES02_92724)
ES02_92724df$UTC <- as.POSIXct(ES02_92724df$UTC)
ES02_92724df <-ES02_92724df %>%
  left_join(ES02_unknownPulse_minOL, by= "UTC")
ES02_92724df$hour <- hour(ES02_92724df$UTC)
ES02_92724df <- ES02_92724df %>%
  filter(ES02_92724df$hour== c("23"))
ES02_92724Med <- ES02_92724df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
ES02_92724Med$site <- "ES02"

ES02_unknownPulse_peaks <- ES02_92724Med

ES02_unknownPulse_peaks <- ES02_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES02_unknownPulse_peaks$month_day <- paste(ES02_unknownPulse_peaks$month, ES02_unknownPulse_peaks$day, sep = "-")
ES02_unknownPulse_peaks$shore <- "Mid-shore"
ES02_unknownPulse_peaks$lat <- "Eastern"

  #CB02 peak days####
#CB02_10522 <-  format(seq(ymd_hms("2022-10-04 20:00:00"), ymd_hms("2022-10-05 19:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB02_10522df <- data.frame(UTC= CB02_10522)
#CB02_10522df$UTC <- as.POSIXct(CB02_10522df$UTC)
#CB02_10522df <-CB02_10522df %>%
#  left_join(CB02_unknownPulse_minOL, by= "UTC")
#CB02_10522df$hour <- hour(CB02_10522df$UTC)
#CB02_10522df <- CB02_10522df %>%
#  filter(CB02_10522df$hour== c("0"))
#CB02_10522Med <- CB02_10522df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB02_10522Med$site <- "CB02"

CB02_92723 <-  format(seq(ymd_hms("2023-09-27 00:00:00"), ymd_hms("2023-09-27 23:45:00"), by = "15 min"))
CB02_92723df <- data.frame(UTC= CB02_92723)
CB02_92723df$UTC <- as.POSIXct(CB02_92723df$UTC)
CB02_92723df <- CB02_92723df %>%
  left_join(CB02_unknownPulse_minOL, by= "UTC")
CB02_92723df$hour <- hour(CB02_92723df$UTC)
CB02_92723df <- CB02_92723df %>%
  filter(CB02_92723df$hour== c("23"))
CB02_92723Med <- CB02_92723df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB02_92723Med$site <- "CB02"

CB02_92424 <-  format(seq(ymd_hms("2024-09-24 00:00:00"), ymd_hms("2024-09-24 23:45:00"), by = "15 min"))
CB02_92424df <- data.frame(UTC= CB02_92424)
CB02_92424df$UTC <- as.POSIXct(CB02_92424df$UTC)
CB02_92424df <- CB02_92424df %>%
  left_join(CB02_unknownPulse_minOL, by= "UTC")
CB02_92424df$hour <- hour(CB02_92424df$UTC)
CB02_92424df <- CB02_92424df %>%
  filter(CB02_92424df$hour== c("23"))
CB02_92424Med <- CB02_92424df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB02_92424Med$site <- "CB02"

CB02_unknownPulse_peaks <- CB02_92723Med %>%
  full_join(CB02_92424Med)
 
CB02_unknownPulse_peaks <- CB02_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB02_unknownPulse_peaks$month_day <- paste(CB02_unknownPulse_peaks$month, CB02_unknownPulse_peaks$day, sep = "-")
CB02_unknownPulse_peaks$shore <- "Mid-shore"
CB02_unknownPulse_peaks$lat <- "Chesapeake"

  #CB03 peak days####
#CB03_93022 <-  format(seq(ymd_hms("2022-09-29 20:00:00"), ymd_hms("2022-09-30 19:45:00"), by = "15 min"))
#CB03_93022df <- data.frame(UTC= CB03_93022)
#CB03_93022df$UTC <- as.POSIXct(CB03_93022df$UTC)
#CB03_93022df <- CB03_93022df %>%
#  left_join(CB03_unknownPulse_minOL, by= "UTC")
#CB03_93022df$hour <- hour(CB03_93022df$UTC)
#CB03_93022df <- CB03_93022df %>%
#  filter(CB03_93022df$hour== c("23"))
#CB03_93022Med <- CB03_93022df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_500= median(OL_500, na.rm= TRUE))
#CB03_93022Med$site <- "CB03"
#CB03_93022Med$season <- "Fall"

CB03_92423 <-  format(seq(ymd_hms("2023-09-24 00:00:00"), ymd_hms("2023-09-24 23:45:00"), by = "15 min"))
CB03_92423df <- data.frame(UTC= CB03_92423)
CB03_92423df$UTC <- as.POSIXct(CB03_92423df$UTC)
CB03_92423df <- CB03_92423df %>%
  left_join(CB03_unknownPulse_minOL, by= "UTC")
CB03_92423df$hour <- hour(CB03_92423df$UTC)
CB03_92423df <- CB03_92423df %>%
  filter(CB03_92423df$hour== c("0"))
CB03_92423Med <- CB03_92423df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB03_92423Med$site <- "CB03"
CB03_92423Med$season <- "Fall"

CB03_92624 <-  format(seq(ymd_hms("2024-09-26 00:00:00"), ymd_hms("2024-09-26 23:45:00"), by = "15 min"))
CB03_92624df <- data.frame(UTC= CB03_92624)
CB03_92624df$UTC <- as.POSIXct(CB03_92624df$UTC)
CB03_92624df <- CB03_92624df %>%
  left_join(CB03_unknownPulse_minOL, by= "UTC")
CB03_92624df$hour <- hour(CB03_92624df$UTC)
CB03_92624df <- CB03_92624df %>%
  filter(CB03_92624df$hour== c("23"))
CB03_92624Med <- CB03_92624df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_500= median(OL_500, na.rm= TRUE))
CB03_92624Med$site <- "CB03"
CB03_92624Med$season <- "Fall"

CB03_unknownPulse_peaks <- CB03_92423Med %>%
  full_join(CB03_92624Med)
 
CB03_unknownPulse_peaks <- CB03_unknownPulse_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB03_unknownPulse_peaks$month_day <- paste(CB03_unknownPulse_peaks$month, CB03_unknownPulse_peaks$day, sep = "-")
CB03_unknownPulse_peaks$shore <- "Mid-shore"
CB03_unknownPulse_peaks$lat <- "Chesapeake"




#combining####
inshore_unknownPulse_peaks <- DB01_unknownPulse_peaks %>%
#  full_join(ES01_unknownPulse_peaks) %>%
  full_join(CB01_unknownPulse_peaks)

midshore_unknownPulse_peaks <- DB02_unknownPulse_peaks %>%
#  full_join(ES02_unknownPulse_peaks) %>%
  full_join(CB02_unknownPulse_peaks) %>%
  full_join(CB03_unknownPulse_peaks)

all_unknownPulse_peaks <- inshore_unknownPulse_peaks %>%
  full_join(midshore_unknownPulse_peaks)

```
#Chorus onset: cusk eel
```{r}
#Cusk eel####
  #DB01- onset days:8/17/2022, 6/28/2023, 8/19/2024####
#DB01_81722 <-  format(seq(ymd_hms("2022-08-17 00:00:00"), ymd_hms("2022-08-17 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#DB01_81722df <- data.frame(UTC= DB01_81722)
#DB01_81722df$UTC <- as.POSIXct(DB01_81722df$UTC)
#DB01_81722df <-DB01_81722df %>%
#  left_join(DB01_cuskEel_minOL, by= "UTC")
#DB01_81722df$hour <- hour(DB01_81722df$UTC)
#DB01_81722df <- DB01_81722df %>%
 # filter(DB01_81722df$hour== c("23"))
#DB01_81722Med <- DB01_81722df%>%
#  dplyr::group_by(hour, UTC_date)%>%
 # dplyr::summarise(
 #   med_2000= median(OL_2000, na.rm= TRUE))
#DB01_81722Med$site <- "DB01"
#DB01_81722Med$season <- "Summer"

DB01_62823 <-  format(seq(ymd_hms("2023-06-28 00:00:00"), ymd_hms("2023-06-28 23:45:00"), by = "15 min")) 
DB01_62823df <- data.frame(UTC= DB01_62823)
DB01_62823df$UTC <- as.POSIXct(DB01_62823df$UTC)
DB01_62823df <-DB01_62823df %>%
  left_join(DB01_cuskEel_minOL, by= "UTC")
DB01_62823df$hour <- hour(DB01_62823df$UTC)
DB01_62823df <- DB01_62823df %>%
  filter(DB01_62823df$hour== c("0"))
DB01_62823Med <- DB01_62823df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
DB01_62823Med$site <- "DB01"
DB01_62823Med$season <- "Summer"

DB01_81924 <-  format(seq(ymd_hms("2024-08-19 00:00:00"), ymd_hms("2024-08-19 23:45:00"), by = "15 min")) 
DB01_81924df <- data.frame(UTC= DB01_81924)
DB01_81924df$UTC <- as.POSIXct(DB01_81924df$UTC)
DB01_81924df <-DB01_81924df %>%
  left_join(DB01_cuskEel_minOL, by= "UTC")
DB01_81924df$hour <- hour(DB01_81924df$UTC)
DB01_81924df <- DB01_81924df %>%
  filter(DB01_81924df$hour== c("23"))
DB01_81924Med <- DB01_81924df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
DB01_81924Med$site <- "DB01"
DB01_81924Med$season <- "Summer"

DB01_cuskEel_onsets <- DB01_62823Med %>%
  full_join(DB01_81924Med)

DB01_cuskEel_onsets <- DB01_cuskEel_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB01_cuskEel_onsets$month_day <- paste(DB01_cuskEel_onsets$month, DB01_cuskEel_onsets$day, sep = "-")
DB01_cuskEel_onsets$shore <- "Inshore"
DB01_cuskEel_onsets$lat <- "Delaware"


  #ES01- onset days:8/31/2024####
ES01_83124 <-  format(seq(ymd_hms("2024-08-31 00:00:00"), ymd_hms("2024-08-31 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
ES01_83124df <- data.frame(UTC= ES01_83124)
ES01_83124df$UTC <- as.POSIXct(ES01_83124df$UTC)
ES01_83124df <-ES01_83124df %>%
  left_join(ES01_cuskEel_minOL, by= "UTC")
ES01_83124df$hour <- hour(ES01_83124df$UTC)
ES01_83124df <- ES01_83124df %>%
  filter(ES01_83124df$hour== c("23"))
ES01_83124Med <- ES01_83124df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
ES01_83124Med$site <- "ES01"
ES01_83124Med$season <- "Summer"

ES01_cuskEel_onsets <- ES01_83124Med

ES01_cuskEel_onsets <- ES01_cuskEel_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES01_cuskEel_onsets$month_day <- paste(ES01_cuskEel_onsets$month, ES01_cuskEel_onsets$day, sep = "-")
ES01_cuskEel_onsets$shore <- "Inshore"
ES01_cuskEel_onsets$lat <- "Eastern"

  #CB01- onset days:8/18/2022, 6/2/2023, 7/26/2024####
#CB01_81822 <-  format(seq(ymd_hms("2022-08-18 00:00:00"), ymd_hms("2022-08-18 23:45:00"), by = "15 min")) #weird timezone things so shift by 4 hours
#CB01_81822df <- data.frame(UTC= CB01_81822)
#CB01_81822df$UTC <- as.POSIXct(CB01_81822df$UTC)
#CB01_81822df <-CB01_81822df %>%
#  left_join(CB01_cuskEel_minOL, by= "UTC")
#CB01_81822df$hour <- hour(CB01_81822df$UTC)
#CB01_81822df <- CB01_81822df %>%
#  filter(CB01_81822df$hour== c("23"))
#CB01_81822Med <- CB01_81822df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_2000= median(OL_2000, na.rm= TRUE))
#CB01_81822Med$site <- "CB01"
#CB01_81822Med$season <- "Summer"

CB01_6223 <-  format(seq(ymd_hms("2023-06-02 00:00:00"), ymd_hms("2023-06-02 23:45:00"), by = "15 min")) 
CB01_6223df <- data.frame(UTC= CB01_6223)
CB01_6223df$UTC <- as.POSIXct(CB01_6223df$UTC)
CB01_6223df <-CB01_6223df %>%
  left_join(CB01_cuskEel_minOL, by= "UTC")
CB01_6223df$hour <- hour(CB01_6223df$UTC)
CB01_6223df <- CB01_6223df %>%
  filter(CB01_6223df$hour== c("0"))
CB01_6223Med <- CB01_6223df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
CB01_6223Med$site <- "CB01"
CB01_6223Med$season <- "Summer"

CB01_72624 <-  format(seq(ymd_hms("2024-07-26 00:00:00"), ymd_hms("2024-07-26 23:45:00"), by = "15 min")) 
CB01_72624df <- data.frame(UTC= CB01_72624)
CB01_72624df$UTC <- as.POSIXct(CB01_72624df$UTC)
CB01_72624df <-CB01_72624df %>%
  left_join(CB01_cuskEel_minOL, by= "UTC")
CB01_72624df$hour <- hour(CB01_72624df$UTC)
CB01_72624df <- CB01_72624df %>%
  filter(CB01_72624df$hour== c("0"))
CB01_72624Med <- CB01_72624df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
CB01_72624Med$site <- "CB01"
CB01_72624Med$season <- "Summer"

CB01_cuskEel_onsets <- CB01_6223Med %>%
  full_join(CB01_72624Med)

CB01_cuskEel_onsets <- CB01_cuskEel_onsets %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB01_cuskEel_onsets$month_day <- paste(CB01_cuskEel_onsets$month, CB01_cuskEel_onsets$day, sep = "-")
CB01_cuskEel_onsets$shore <- "Inshore"
CB01_cuskEel_onsets$lat <- "Chesapeake"




#combining ####
all_cuskEel_onsets <- DB01_cuskEel_onsets %>%
#  full_join(ES01_cuskEel_onsets) %>%
  full_join(CB01_cuskEel_onsets)
```
#Chorus peak: cusk eel
```{r}
#Cusk eel####
CB01_cuskEel_minOL$year <- year(CB01_cuskEel_minOL$UTC)
CB01_cuskEel_peaks <- CB01_cuskEel_minOL %>%
  group_by(year) %>%
  slice_max(OL_2000, n= 15)
  #DB01 peak days:9/16/2022 (23:30), 9/10/2023 (23:45), 9/11/2024 (23:45)
  #ES01 peak day: 9/19/2024
  #CB01 peak days: 9/9/2022 (23:30), 9/5/2023 (23:45), 9/10/2024 (0)
  #DB01####
#DB01_91622 <-  format(seq(ymd_hms("2022-09-16 00:00:00"), ymd_hms("2022-09-16 23:45:00"), by = "15 min")) 
#DB01_91622df <- data.frame(UTC= DB01_91622)
#DB01_91622df$UTC <- as.POSIXct(DB01_91622df$UTC)
#DB01_91622df <-DB01_91622df %>%
#  left_join(DB01_cuskEel_minOL, by= "UTC")
#DB01_91622df$hour <- hour(DB01_91622df$UTC)
#DB01_91622df <- DB01_91622df %>%
#  filter(DB01_91622df$hour== c("23"))
#DB01_91622Med <- DB01_91622df%>%
 # dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
#    med_2000= median(OL_2000, na.rm= TRUE))
#DB01_91622Med$site <- "DB01"

DB01_91023 <-  format(seq(ymd_hms("2023-09-10 00:00:00"), ymd_hms("2023-09-10 23:45:00"), by = "15 min")) 
DB01_91023df <- data.frame(UTC= DB01_91023)
DB01_91023df$UTC <- as.POSIXct(DB01_91023df$UTC)
DB01_91023df <-DB01_91023df %>%
  left_join(DB01_cuskEel_minOL, by= "UTC")
DB01_91023df$hour <- hour(DB01_91023df$UTC)
DB01_91023df <- DB01_91023df %>%
  filter(DB01_91023df$hour== c("23"))
DB01_91023Med <- DB01_91023df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
DB01_91023Med$site <- "DB01"

DB01_91124 <-  format(seq(ymd_hms("2024-09-11 00:00:00"), ymd_hms("2024-09-11 23:45:00"), by = "15 min")) 
DB01_91124df <- data.frame(UTC= DB01_91124)
DB01_91124df$UTC <- as.POSIXct(DB01_91124df$UTC)
DB01_91124df <-DB01_91124df %>%
  left_join(DB01_cuskEel_minOL, by= "UTC")
DB01_91124df$hour <- hour(DB01_91124df$UTC)
DB01_91124df <- DB01_91124df %>%
  filter(DB01_91124df$hour== c("23"))
DB01_91124Med <- DB01_91124df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
DB01_91124Med$site <- "DB01"

DB01_cuskEel_peaks <- DB01_91023Med %>%
  full_join(DB01_91124Med)

DB01_cuskEel_peaks <- DB01_cuskEel_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
DB01_cuskEel_peaks$month_day <- paste(DB01_cuskEel_peaks$month, DB01_cuskEel_peaks$day, sep = "-")
DB01_cuskEel_peaks$shore <- "Inshore"
DB01_cuskEel_peaks$lat <- "Delaware"

  #ES01####
ES01_91924 <-  format(seq(ymd_hms("2024-09-19 00:00:00"), ymd_hms("2024-09-19 23:45:00"), by = "15 min")) 
ES01_91924df <- data.frame(UTC= ES01_91924)
ES01_91924df$UTC <- as.POSIXct(ES01_91924df$UTC)
ES01_91924df <-ES01_91924df %>%
  left_join(ES01_cuskEel_minOL, by= "UTC")
ES01_91924df$hour <- hour(ES01_91924df$UTC)
ES01_91924df <- ES01_91924df %>%
  filter(ES01_91924df$hour== c("23"))
ES01_91924Med <- ES01_91924df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
ES01_91924Med$site <- "ES01"

ES01_cuskEel_peaks <- ES01_91924Med 

ES01_cuskEel_peaks <- ES01_cuskEel_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
ES01_cuskEel_peaks$month_day <- paste(ES01_cuskEel_peaks$month, ES01_cuskEel_peaks$day, sep = "-")
ES01_cuskEel_peaks$shore <- "Inshore"
ES01_cuskEel_peaks$lat <- "Eastern"

  #CB01####
#CB01_9922 <-  format(seq(ymd_hms("2022-09-09 00:00:00"), ymd_hms("2022-09-09 23:45:00"), by = "15 min")) 
#CB01_9922df <- data.frame(UTC= CB01_9922)
#CB01_9922df$UTC <- as.POSIXct(CB01_9922df$UTC)
#CB01_9922df <-CB01_9922df %>%
#  left_join(CB01_cuskEel_minOL, by= "UTC")
#CB01_9922df$hour <- hour(CB01_9922df$UTC)
#CB01_9922df <- CB01_9922df %>%
#  filter(CB01_9922df$hour== c("0"))
#CB01_9922Med <- CB01_9922df%>%
#  dplyr::group_by(hour, UTC_date)%>%
#  dplyr::summarise(
 #   med_2000= median(OL_2000, na.rm= TRUE))
#CB01_9922Med$site <- "CB01"

CB01_9523 <-  format(seq(ymd_hms("2023-09-05 00:00:00"), ymd_hms("2023-09-05 23:45:00"), by = "15 min")) 
CB01_9523df <- data.frame(UTC= CB01_9523)
CB01_9523df$UTC <- as.POSIXct(CB01_9523df$UTC)
CB01_9523df <-CB01_9523df %>%
  left_join(CB01_cuskEel_minOL, by= "UTC")
CB01_9523df$hour <- hour(CB01_9523df$UTC)
CB01_9523df <- CB01_9523df %>%
  filter(CB01_9523df$hour== c("23"))
CB01_9523Med <- CB01_9523df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
CB01_9523Med$site <- "CB01"

CB01_91024 <-  format(seq(ymd_hms("2024-09-10 00:00:00"), ymd_hms("2024-09-10 23:45:00"), by = "15 min")) 
CB01_91024df <- data.frame(UTC= CB01_91024)
CB01_91024df$UTC <- as.POSIXct(CB01_91024df$UTC)
CB01_91024df <-CB01_91024df %>%
  left_join(CB01_cuskEel_minOL, by= "UTC")
CB01_91024df$hour <- hour(CB01_91024df$UTC)
CB01_91024df <- CB01_91024df %>%
  filter(CB01_91024df$hour== c("0"))
CB01_91024Med <- CB01_91024df%>%
  dplyr::group_by(hour, UTC_date)%>%
  dplyr::summarise(
    med_2000= median(OL_2000, na.rm= TRUE))
CB01_91024Med$site <- "CB01"

CB01_cuskEel_peaks <- CB01_9523Med %>%
  full_join(CB01_91024Med)

CB01_cuskEel_peaks <- CB01_cuskEel_peaks %>%
  mutate(year = str_split(UTC_date,"-", simplify = T)[,1])%>%
  mutate(month =  str_split(UTC_date,"-", simplify = T)[,2]) %>%
  mutate(day = str_split(UTC_date, "-", simplify= T)[,3])
CB01_cuskEel_peaks$month_day <- paste(CB01_cuskEel_peaks$month, CB01_cuskEel_peaks$day, sep = "-")
CB01_cuskEel_peaks$shore <- "Inshore"
CB01_cuskEel_peaks$lat <- "Chesapeake"

#combining####
all_cuskEel_peaks <- DB01_cuskEel_peaks %>%
#  full_join(ES01_cuskEel_peaks) %>%
  full_join(CB01_cuskEel_peaks)
```
#Error bar plot: unknown pulse onset
```{r}
#separating dates out
all_unknownPulse_onsetDateSummary <- all_unknownPulse_onsets %>%
  mutate(
    date= ymd(UTC_date),
    days_since_January = as.numeric(date- ymd(paste(year(UTC_date), 1, 1, sep= "-")))
  ) %>%
  group_by(site) %>%
  summarize(across(days_since_January, median), .groups= "keep") %>%
  mutate(median_month_date = format(ymd("2023-01-01") + days(floor(days_since_January)), "%m-%d"))
all_unknownPulse_onsetDateMax <- all_unknownPulse_onsets %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
all_unknownPulse_onsetDateMin <- all_unknownPulse_onsets %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
  
#first get med SPL of the onset dates
all_unknownPulse_onsetSPLSummary <- all_unknownPulse_onsets %>%
  dplyr:: group_by(site) %>%
  dplyr:: summarize(
    med_500 = median(med_500)
  )
#only 1 value of each of these, but still separate out the min and max SPL values
all_unknownPulse_onsetSPLMax <- all_unknownPulse_onsets %>%
  group_by(site) %>%
  summarize(max_500= max(med_500))
all_unknownPulse_onsetSPLMin <- all_unknownPulse_onsets %>%
  group_by(site) %>%
  summarize(min_500= min(med_500))
#put all together
all_unknownPulse_onsetSummary <- all_unknownPulse_onsetDateSummary %>%
  full_join(all_unknownPulse_onsetSPLSummary) %>%
  full_join(all_unknownPulse_onsetSPLMax) %>%
  full_join(all_unknownPulse_onsetSPLMin) %>%
  full_join(all_unknownPulse_onsetDateMax) %>%
  full_join(all_unknownPulse_onsetDateMin)

#had to separate out ES sites since there was only 1 day and it messed up its date
ES_unknownPulse_onsets <- ES01_unknownPulse_onsets %>%
  full_join(ES02_unknownPulse_onsets)
ES_unknownPulse_onsetsDateMin <- ES_unknownPulse_onsets %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
ES_unknownPulse_onsetsDateMax <- ES_unknownPulse_onsets %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
ES_unknownPulse_onsets <- ES_unknownPulse_onsets [-c(1,2,5:8, 10, 11)]
colnames(ES_unknownPulse_onsets )[3] <- "median_month_date"
ES_unknownPulse_onsets <- ES_unknownPulse_onsets %>%
  full_join(ES_unknownPulse_onsetsDateMax) %>%
  full_join(ES_unknownPulse_onsetsDateMin)

all_unknownPulse_onsetSummary <- all_unknownPulse_onsetSummary %>%
  full_join(ES_unknownPulse_onsets)

all_unknownPulse_onsetSummary$site = factor(all_unknownPulse_onsetSummary$site,
                                        levels= c('DB01', 'DB02', 'ES01', 'ES02', 'CB01', 'CB02', 'CB03'))
all_unknownPulse_onsetSummary$lat = case_when(all_unknownPulse_onsetSummary$site == "DB01" ~ "38.71",
                            all_unknownPulse_onsetSummary$site == "DB02" ~ "38.48",
                            all_unknownPulse_onsetSummary$site == "ES01" ~ "37.69",
                            all_unknownPulse_onsetSummary$site == "ES02" ~ "37.68",
                            all_unknownPulse_onsetSummary$site == "CB01" ~ "36.98",
                            all_unknownPulse_onsetSummary$site == "CB02" ~ "36.98",
                            all_unknownPulse_onsetSummary$site == "CB03" ~ "36.51")

# all_unknownPulse_onsetSummary$lat = factor(all_unknownPulse_onsetSummary$lat,
#                                         levels= c('Delaware', 'Eastern', 'Chesapeake'))

all_unknownPulse_onsetSummary$long = case_when(all_unknownPulse_onsetSummary$site == "DB01" ~ "-74.82",
                            all_unknownPulse_onsetSummary$site == "DB02" ~ "-74.47",
                            all_unknownPulse_onsetSummary$site == "ES01" ~ "-75.29",
                            all_unknownPulse_onsetSummary$site == "ES02" ~ "-74.83",
                            all_unknownPulse_onsetSummary$site == "CB01" ~ "-75.67",
                            all_unknownPulse_onsetSummary$site == "CB02" ~ "-75.22",
                            all_unknownPulse_onsetSummary$site == "CB03" ~ "-75.31")

all_unknownPulse_onsetSummary$shore = case_when(all_unknownPulse_onsetSummary$site == "DB01" ~ "Inshore",
                            all_unknownPulse_onsetSummary$site == "DB02" ~ "Mid-shore",
                            all_unknownPulse_onsetSummary$site == "ES01" ~ "Inshore",
                            all_unknownPulse_onsetSummary$site == "ES02" ~ "Mid-shore",
                            all_unknownPulse_onsetSummary$site == "CB01" ~ "Inshore",
                            all_unknownPulse_onsetSummary$site == "CB02" ~ "Mid-shore",
                            all_unknownPulse_onsetSummary$site == "CB03" ~ "Mid-shore")

all_unknownPulse_onsetSummary$depth = case_when(all_unknownPulse_onsetSummary$site == "DB01" ~ "17.1",
                            all_unknownPulse_onsetSummary$site == "DB02" ~ "38.1",
                            all_unknownPulse_onsetSummary$site == "ES01" ~ "20",
                            all_unknownPulse_onsetSummary$site == "ES02" ~ "40.5",
                            all_unknownPulse_onsetSummary$site == "CB01" ~ "18.6",
                            all_unknownPulse_onsetSummary$site == "CB02" ~ "34.1",
                            all_unknownPulse_onsetSummary$site == "CB03" ~ "22.6")

ggplot(all_unknownPulse_onsetSummary, aes(x = median_month_date, y = med_500, color = site, shape= lat)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = min_500, ymax = max_500), width = 0.05) + # Vertical error bars
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  scale_color_manual(values=c("DB01" = "#001743",
                              "DB02" = "#B71300",
                              "ES01" = "#0085CA",
                              "ES02" = "#DB6015",
                              "CB01" = "#5EB6D9",
                              "CB02" = "#FFAB28",
                              "CB03" = "#FFDD6A"),
                     name = "Site") +
 guides(shape= guide_legend(title= "Latitude"), color= guide_legend(title= "Site"))+
  labs(x = "Onset Date", title= "Unknown Pulse: Onset by site") +
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  theme_bw() +
  theme(axis.title.y=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=15, color="black"),
        axis.text.x=element_text(size=15, color="black"),
        strip.text=element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=16))

all_unknownPulse_onsetSummary$median_month_date <- as.Date(all_unknownPulse_onsetSummary$median_month_date, format= "%m-%d")
all_unknownPulse_onsetSummary$min_date <- as.Date(all_unknownPulse_onsetSummary$min_date, format= "%m-%d")
all_unknownPulse_onsetSummary$max_date <- as.Date(all_unknownPulse_onsetSummary$max_date, format= "%m-%d")


Lat_plot <- ggplot(all_unknownPulse_onsetSummary, aes(x= median_month_date, y= lat, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Median onset date of chorusing", y= "Latitude")+
#  scale_x_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))


Long_plot <- ggplot(all_unknownPulse_onsetSummary, aes(x= long, y= median_month_date, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(ymin = min_date, ymax = max_date), width= 0.05) + 
  scale_x_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Longitude", y= "Median onset date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))

depth_plot <- ggplot(all_unknownPulse_onsetSummary, aes(x= median_month_date, y= depth, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), width= 0.05) + 
    scale_y_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
#  labs(x= "Depth", y= "Median onset date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))

Lat_plot/Long_plot + plot_layout(guides= "collect")
depth_plot

```
#Error bar plot: unknown pulse peak
```{r}
all_unknownPulse_peakDateSummary <- all_unknownPulse_peaks %>%
  mutate(
    date= ymd(UTC_date),
    days_since_January = as.numeric(date- ymd(paste(year(UTC_date), 1, 1, sep= "-")))
  ) %>%
  group_by(site) %>%
  summarize(across(days_since_January, median), .groups= "keep") %>%
  mutate(median_month_date = format(ymd("2023-01-01") + days(floor(days_since_January)), "%m-%d"))
all_unknownPulse_peakDateMax <- all_unknownPulse_peaks %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
all_unknownPulse_peakDateMin <- all_unknownPulse_peaks %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
  
#first get med SPL of the peak dates
all_unknownPulse_peakSPLSummary <- all_unknownPulse_peaks %>%
  dplyr:: group_by(site) %>%
  dplyr:: summarize(
    med_500 = median(med_500)
  )
#only 1 value of each of these, but still separate out the min and max SPL values
all_unknownPulse_peakSPLMax <- all_unknownPulse_peaks %>%
  group_by(site) %>%
  summarize(max_500= max(med_500))
all_unknownPulse_peakSPLMin <- all_unknownPulse_peaks %>%
  group_by(site) %>%
  summarize(min_500= min(med_500))
#put all together
all_unknownPulse_peakSummary <- all_unknownPulse_peakDateSummary %>%
  full_join(all_unknownPulse_peakSPLSummary) %>%
  full_join(all_unknownPulse_peakSPLMax) %>%
  full_join(all_unknownPulse_peakSPLMin) %>%
  full_join(all_unknownPulse_peakDateMax) %>%
  full_join(all_unknownPulse_peakDateMin)

#had to separate out ES sites since there was only 1 day and it messed up its date
ES_unknownPulse_peaks <- ES01_unknownPulse_peaks %>%
  full_join(ES02_unknownPulse_peaks)
ES_unknownPulse_peaksDateMin <- ES_unknownPulse_peaks %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
ES_unknownPulse_peaksDateMax <- ES_unknownPulse_peaks %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
ES_unknownPulse_peaks <- ES_unknownPulse_peaks [-c(1,5:7, 9, 10)]
colnames(ES_unknownPulse_peaks )[4] <- "median_month_date"
ES_unknownPulse_peaks <- ES_unknownPulse_peaks %>%
  full_join(ES_unknownPulse_peaksDateMax) %>%
  full_join(ES_unknownPulse_peaksDateMin)
all_unknownPulse_peakSummary <- all_unknownPulse_peakSummary %>%
  full_join(ES_unknownPulse_peaks)

all_unknownPulse_peakSummary$site = factor(all_unknownPulse_peakSummary$site,
                                        levels= c('DB01', 'DB02', 'ES01', 'ES02', 'CB01', 'CB02', 'CB03'))
# all_unknownPulse_peakSummary$lat = case_when(all_unknownPulse_peakSummary$site == "DB01" ~ "Delaware",
#                             all_unknownPulse_peakSummary$site == "DB02" ~ "Delaware",
#                             all_unknownPulse_peakSummary$site == "ES01" ~ "Eastern",
#                             all_unknownPulse_peakSummary$site == "ES02" ~ "Eastern",
#                             all_unknownPulse_peakSummary$site == "CB01" ~ "Chesapeake",
#                             all_unknownPulse_peakSummary$site == "CB02" ~ "Chesapeake",
#                             all_unknownPulse_peakSummary$site == "CB03" ~ "Chesapeake")

all_unknownPulse_peakSummary$lat = case_when(all_unknownPulse_peakSummary$site == "DB01" ~ "38.71",
                            all_unknownPulse_peakSummary$site == "DB02" ~ "38.48",
                            all_unknownPulse_peakSummary$site == "ES01" ~ "37.69",
                            all_unknownPulse_peakSummary$site == "ES02" ~ "37.68",
                            all_unknownPulse_peakSummary$site == "CB01" ~ "36.98",
                            all_unknownPulse_peakSummary$site == "CB02" ~ "36.98",
                            all_unknownPulse_peakSummary$site == "CB03" ~ "36.51")

all_unknownPulse_peakSummary$long = case_when(all_unknownPulse_peakSummary$site == "DB01" ~ "-74.82",
                            all_unknownPulse_peakSummary$site == "DB02" ~ "-74.47",
                            all_unknownPulse_peakSummary$site == "ES01" ~ "-75.29",
                            all_unknownPulse_peakSummary$site == "ES02" ~ "-74.83",
                            all_unknownPulse_peakSummary$site == "CB01" ~ "-75.67",
                            all_unknownPulse_peakSummary$site == "CB02" ~ "-75.22",
                            all_unknownPulse_peakSummary$site == "CB03" ~ "-75.31")

all_unknownPulse_peakSummary$shore = case_when(all_unknownPulse_peakSummary$site == "DB01" ~ "Inshore",
                            all_unknownPulse_peakSummary$site == "DB02" ~ "Mid-shore",
                            all_unknownPulse_peakSummary$site == "ES01" ~ "Inshore",
                            all_unknownPulse_peakSummary$site == "ES02" ~ "Mid-shore",
                            all_unknownPulse_peakSummary$site == "CB01" ~ "Inshore",
                            all_unknownPulse_peakSummary$site == "CB02" ~ "Mid-shore",
                            all_unknownPulse_peakSummary$site == "CB03" ~ "Mid-shore")

# all_unknownPulse_peakSummary$lat = factor(all_unknownPulse_peakSummary$lat,
#                                         levels= c('Delaware', 'Eastern', 'Chesapeake'))

ggplot(all_unknownPulse_peakSummary, aes(x = median_month_date, y = med_500, color = site, shape= lat)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = min_500, ymax = max_500), width = 0.05) + # Vertical error bars
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  scale_color_manual(values=c("DB01" = "#001743",
                              "DB02" = "#B71300",
                              "ES01" = "#0085CA",
                              "ES02" = "#DB6015",
                              "CB01" = "#5EB6D9",
                              "CB02" = "#FFAB28",
                              "CB03" = "#FFDD6A"),
                     name = "Site") +
  guides(shape= guide_legend(title= "Latitude"), color= guide_legend(title= "Site"))+
  labs(x = "peak Date", title= "Unknown Pulse: peak by site") +
  ylab(expression(paste('Median 500Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  theme_bw() +
  theme(axis.title.y=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=15, color="black"),
        axis.text.x=element_text(size=15, color="black"),
        strip.text=element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=16))


all_unknownPulse_peakSummary$median_month_date <- as.Date(all_unknownPulse_peakSummary$median_month_date, format= "%m-%d")
all_unknownPulse_peakSummary$min_date <- as.Date(all_unknownPulse_peakSummary$min_date, format= "%m-%d")
all_unknownPulse_peakSummary$max_date <- as.Date(all_unknownPulse_peakSummary$max_date, format= "%m-%d")


Lat_plot <- ggplot(all_unknownPulse_peakSummary, aes(x= median_month_date, y= lat, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Median peak date of chorusing", y= "Latitude")+
#  scale_x_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))


Long_plot <- ggplot(all_unknownPulse_peakSummary, aes(x= long, y= median_month_date, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(ymin = min_date, ymax = max_date), width= 0.05) + 
  scale_x_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Longitude", y= "Median peak date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))

Lat_plot/Long_plot + plot_layout(guides= "collect")
```
#Error bar plot: cusk eel onset
```{r}
#separating dates out
all_cuskEel_onsetDateSummary <- all_cuskEel_onsets %>%
  mutate(
    date= ymd(UTC_date),
    days_since_January = as.numeric(date- ymd(paste(year(UTC_date), 1, 1, sep= "-")))
  ) %>%
  group_by(site) %>%
  summarize(across(days_since_January, median), .groups= "keep") %>%
  mutate(median_month_date = format(ymd("2023-01-01") + days(floor(days_since_January)), "%m-%d"))
all_cuskEel_onsetDateMax <- all_cuskEel_onsets %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
all_cuskEel_onsetDateMin <- all_cuskEel_onsets %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
  
#first get med SPL of the onset dates
all_cuskEel_onsetSPLSummary <- all_cuskEel_onsets %>%
  dplyr:: group_by(site) %>%
  dplyr:: summarize(
    med_2000 = median(med_2000)
  )
#only 1 value of each of these, but still separate out the min and max SPL values
all_cuskEel_onsetSPLMax <- all_cuskEel_onsets %>%
  group_by(site) %>%
  summarize(max_2000= max(med_2000))
all_cuskEel_onsetSPLMin <- all_cuskEel_onsets %>%
  group_by(site) %>%
  summarize(min_2000= min(med_2000))
#put all together
all_cuskEel_onsetSummary <- all_cuskEel_onsetDateSummary %>%
  full_join(all_cuskEel_onsetSPLSummary) %>%
  full_join(all_cuskEel_onsetSPLMax) %>%
  full_join(all_cuskEel_onsetSPLMin) %>%
  full_join(all_cuskEel_onsetDateMax) %>%
  full_join(all_cuskEel_onsetDateMin)

#had to separate out ES sites since there was only 1 day and it messed up its date
colnames(ES01_cuskEel_onsets )[9] <- "median_month_date"
ES01_cuskEel_onsetsDateMin <- ES01_cuskEel_onsets %>%
  group_by(site) %>%
  summarize(min_date= min(median_month_date))
ES01_cuskEel_onsetsDateMax <- ES01_cuskEel_onsets %>%
  group_by(site) %>%
  summarize(max_date= max(median_month_date))
ES01_cuskEel_onsets <- ES01_cuskEel_onsets [-c(1,2,5:8, 10, 11)]

ES01_cuskEel_onsets <- ES01_cuskEel_onsets %>%
  full_join(ES01_cuskEel_onsetsDateMax) %>%
  full_join(ES01_cuskEel_onsetsDateMin)

all_cuskEel_onsetSummary <- all_cuskEel_onsetSummary %>%
  full_join(ES01_cuskEel_onsets)

all_cuskEel_onsetSummary$site = factor(all_cuskEel_onsetSummary$site,
                                        levels= c('DB01', 'ES01',  'CB01'))


all_cuskEel_onsetSummary$lat = case_when(all_cuskEel_onsetSummary$site == "DB01" ~ "38.71",
                            all_cuskEel_onsetSummary$site == "ES01" ~ "37.69",
                            all_cuskEel_onsetSummary$site == "CB01" ~ "36.98")


all_cuskEel_onsetSummary$long = case_when(all_cuskEel_onsetSummary$site == "DB01" ~ "-74.82",
                            all_cuskEel_onsetSummary$site == "ES01" ~ "-75.29",
                            all_cuskEel_onsetSummary$site == "CB01" ~ "-75.67")

all_cuskEel_onsetSummary$shore = case_when(all_cuskEel_onsetSummary$site == "DB01" ~ "Inshore",
                            all_cuskEel_onsetSummary$site == "DB02" ~ "Mid-shore",
                            all_cuskEel_onsetSummary$site == "ES01" ~ "Inshore",
                            all_cuskEel_onsetSummary$site == "ES02" ~ "Mid-shore",
                            all_cuskEel_onsetSummary$site == "CB01" ~ "Inshore",
                            all_cuskEel_onsetSummary$site == "CB02" ~ "Mid-shore",
                            all_cuskEel_onsetSummary$site == "CB03" ~ "Mid-shore")

all_cuskEel_onsetSummary$depth = case_when(all_cuskEel_onsetSummary$site == "DB01" ~ "17.1",
                            all_cuskEel_onsetSummary$site == "DB02" ~ "38.1",
                            all_cuskEel_onsetSummary$site == "ES01" ~ "20",
                            all_cuskEel_onsetSummary$site == "ES02" ~ "40.5",
                            all_cuskEel_onsetSummary$site == "CB01" ~ "18.6",
                            all_cuskEel_onsetSummary$site == "CB02" ~ "34.1",
                            all_cuskEel_onsetSummary$site == "CB03" ~ "22.6")


ggplot(all_cuskEel_onsetSummary, aes(x = median_month_date, y = med_2000, color = site, shape= lat)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = min_2000, ymax = max_2000), width = 0.05) + # Vertical error bars
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  scale_color_manual(values=c("DB01" = "#001743",
                              "ES01" = "#0085CA",
                              "CB01" = "#5EB6D9"),
                     name = "Site") +
 guides(shape= guide_legend(title= "Latitude"), color= guide_legend(title= "Site"))+
  labs(x = "Onset Date", title= "Cusk Eel: Onset by site") +
  ylab(expression(paste('Median 2000Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  theme_bw() +
  theme(axis.title.y=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=15, color="black"),
        axis.text.x=element_text(size=15, color="black"),
        strip.text=element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=16))

all_cuskEel_onsetSummary$median_month_date <- as.Date(all_cuskEel_onsetSummary$median_month_date, format= "%m-%d")
all_cuskEel_onsetSummary$min_date <- as.Date(all_cuskEel_onsetSummary$min_date, format= "%m-%d")
all_cuskEel_onsetSummary$max_date <- as.Date(all_cuskEel_onsetSummary$max_date, format= "%m-%d")


Lat_plot <- ggplot(all_cuskEel_onsetSummary, aes(x= median_month_date, y= lat, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Median onset date of chorusing", y= "Latitude")+
#  scale_x_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  theme(legend.position="none")+
  scale_color_manual(values= c("#5761C0"))


Long_plot <- ggplot(all_cuskEel_onsetSummary, aes(x= long, y= median_month_date, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(ymin = min_date, ymax = max_date), width= 0.05) + 
  scale_x_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Longitude", y= "Median onset date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  theme(legend.position="none")+
  scale_color_manual(values= c("#5761C0"))

Long_plot

depth_plot <- ggplot(all_cuskEel_onsetSummary, aes(x= median_month_date, y= depth, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), width= 0.05) + 
    scale_y_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
#  labs(x= "Depth", y= "Median onset date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  guides(color= guide_legend(title= "Proximity to shore"))+
  scale_color_manual(values= c("#5761C0", "#FFAB38"))

depth_plot

```
#Error bar plot" cusk eel peak
```{r}

#separating dates out
all_cuskEel_peakDateSummary <- all_cuskEel_peaks %>%
  mutate(
    date= ymd(UTC_date),
    days_since_January = as.numeric(date- ymd(paste(year(UTC_date), 1, 1, sep= "-")))
  ) %>%
  group_by(site) %>%
  summarize(across(days_since_January, median), .groups= "keep") %>%
  mutate(median_month_date = format(ymd("2023-01-01") + days(floor(days_since_January)), "%m-%d"))
all_cuskEel_peakDateMax <- all_cuskEel_peaks %>%
  group_by(site)%>%
  summarize(max_date= max(month_day))
all_cuskEel_peakDateMin <- all_cuskEel_peaks %>%
  group_by(site)%>%
  summarize(min_date= min(month_day))
  
#first get med SPL of the peak dates
all_cuskEel_peakSPLSummary <- all_cuskEel_peaks %>%
  dplyr:: group_by(site) %>%
  dplyr:: summarize(
    med_2000 = median(med_2000)
  )
#only 1 value of each of these, but still separate out the min and max SPL values
all_cuskEel_peakSPLMax <- all_cuskEel_peaks %>%
  group_by(site) %>%
  summarize(max_2000= max(med_2000))
all_cuskEel_peakSPLMin <- all_cuskEel_peaks %>%
  group_by(site) %>%
  summarize(min_2000= min(med_2000))
#put all together
all_cuskEel_peakSummary <- all_cuskEel_peakDateSummary %>%
  full_join(all_cuskEel_peakSPLSummary) %>%
  full_join(all_cuskEel_peakSPLMax) %>%
  full_join(all_cuskEel_peakSPLMin) %>%
  full_join(all_cuskEel_peakDateMax) %>%
  full_join(all_cuskEel_peakDateMin)

#had to separate out ES sites since there was only 1 day and it messed up its date
colnames(ES01_cuskEel_peaks )[8] <- "median_month_date"
ES01_cuskEel_peaksDateMin <- ES01_cuskEel_peaks %>%
  group_by(site) %>%
  summarize(min_date= min(median_month_date))
ES01_cuskEel_peaksDateMax <- ES01_cuskEel_peaks %>%
  group_by(site) %>%
  summarize(max_date= max(median_month_date))
ES01_cuskEel_peaks <- ES01_cuskEel_peaks [-c(1,2,5:7, 9, 10)]

ES01_cuskEel_peaks <- ES01_cuskEel_peaks %>%
  full_join(ES01_cuskEel_peaksDateMax) %>%
  full_join(ES01_cuskEel_peaksDateMin)

all_cuskEel_peakSummary <- all_cuskEel_peakSummary %>%
  full_join(ES01_cuskEel_peaks)

all_cuskEel_peakSummary$site = factor(all_cuskEel_peakSummary$site,
                                        levels= c('DB01', 'ES01',  'CB01'))
all_cuskEel_peakSummary$lat = case_when(all_cuskEel_peakSummary$site == "DB01" ~ "Delaware",
                            all_cuskEel_peakSummary$site == "ES01" ~ "Eastern",
                            all_cuskEel_peakSummary$site == "CB01" ~ "Chesapeake")

all_cuskEel_peakSummary$lat = factor(all_cuskEel_peakSummary$lat,
                                        levels= c('Delaware', 'Eastern', 'Chesapeake'))

all_cuskEel_peakSummary$lat = case_when(all_cuskEel_peakSummary$site == "DB01" ~ "38.71",
                            all_cuskEel_peakSummary$site == "ES01" ~ "37.69",
                            all_cuskEel_peakSummary$site == "CB01" ~ "36.98")


all_cuskEel_peakSummary$long = case_when(all_cuskEel_peakSummary$site == "DB01" ~ "-74.82",
                            all_cuskEel_peakSummary$site == "ES01" ~ "-75.29",
                            all_cuskEel_peakSummary$site == "CB01" ~ "-75.67")

all_cuskEel_peakSummary$shore = case_when(all_cuskEel_peakSummary$site == "DB01" ~ "Inshore",
                            all_cuskEel_peakSummary$site == "DB02" ~ "Mid-shore",
                            all_cuskEel_peakSummary$site == "ES01" ~ "Inshore",
                            all_cuskEel_peakSummary$site == "ES02" ~ "Mid-shore",
                            all_cuskEel_peakSummary$site == "CB01" ~ "Inshore",
                            all_cuskEel_peakSummary$site == "CB02" ~ "Mid-shore",
                            all_cuskEel_peakSummary$site == "CB03" ~ "Mid-shore")


ggplot(all_cuskEel_peakSummary, aes(x = median_month_date, y = med_2000, color = site, shape= lat)) +
  geom_point(size = 5) +
  geom_errorbar(aes(ymin = min_2000, ymax = max_2000), width = 0.05) + # Vertical error bars
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  scale_color_manual(values=c("DB01" = "#001743",
                              "DB02" = "#B71300",
                              "ES01" = "#0085CA",
                              "ES02" = "#DB6015",
                              "CB01" = "#5EB6D9",
                              "CB02" = "#FFAB28",
                              "CB03" = "#FFDD6A"),
                     name = "Site") +
 guides(color= guide_legend(title= "Site"), shape= guide_legend(title= "Latitude"))+
  labs(x = "Peak Date", title= "Cusk Eel: Peak by site") +
  ylab(expression(paste('Median 2000Hz Octave Level SPL (db re 1 \u00b5Pa)')))+
  theme_bw() +
  theme(axis.title.y=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=15, color="black"),
        axis.text.x=element_text(size=15, color="black"),
        strip.text=element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=16))

all_cuskEel_peakSummary$median_month_date <- as.Date(all_cuskEel_peakSummary$median_month_date, format= "%m-%d")
all_cuskEel_peakSummary$min_date <- as.Date(all_cuskEel_peakSummary$min_date, format= "%m-%d")
all_cuskEel_peakSummary$max_date <- as.Date(all_cuskEel_peakSummary$max_date, format= "%m-%d")


Lat_plot <- ggplot(all_cuskEel_peakSummary, aes(x= median_month_date, y= lat, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(xmin = min_date, xmax = max_date), height = 0.05, orientation = "y") + 
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Median peak date of chorusing", y= "Latitude")+
#  scale_x_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  theme(legend.position="none")+
  scale_color_manual(values= c("#5761C0"))


Long_plot <- ggplot(all_cuskEel_peakSummary, aes(x= long, y= median_month_date, color= shore))+
  geom_point(size= 5)+
  geom_errorbar(aes(ymin = min_date, ymax = max_date), width= 0.05) + 
  scale_x_discrete(limits= rev)+
  directlabels::geom_dl(aes(label = site), method = "smart.grid")+
  theme_bw()+
  labs(x= "Longitude", y= "Median peak date of chorusing")+
#  scale_y_date(limits= as.Date(c("05-01", "10-01"), format= "%m-%d"), date_breaks= "1 month", date_labels = "%m/%d")+
  theme(legend.position="none")+
  scale_color_manual(values= c("#5761C0"))

Long_plot

```